---
title: "ARIMA Model EUR and GBP"
author: "Jane"
date: "01/05/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

# Forcasting Exchange Rate Using ARIMA Model for EUR And GBP
## Reading EUR and GBP Currency into r


```{r}
library(readr)
library(dplyr)
EURGBPARIMA<-  read.csv ("EURGBP_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateEURGBP = ("CLOSE"))

  
head(EURGBPARIMA)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

EURGBPARIMA$Date <- lubridate::ymd(EURGBPARIMA$Date)
head(EURGBPARIMA)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(EURGBPARIMA))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
EURGBPARIMATS<- ts(as.vector(EURGBPARIMA$Rate),  frequency = 322, start= c(2000,01,03))
plot.ts(EURGBPARIMATS)
title("Time Series plot of EURGBPTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```



## Finding the component of the Time Series

```{r}
ComponentEURGBP <- decompose(EURGBPARIMATS)
plot(ComponentEURGBP)
```

## To To achieve stationarity by differencing the data – compute the differences between consecutive observations

```{r}
library("fUnitRoots")
urkpssTest(EURGBPARIMATS, type = c("tau"), lags = c("short"),use.lag = NULL, doplot = TRUE)
EURGBPStationary= diff(EURGBPARIMATS, differences=1)
plot(EURGBPStationary)
```


## Calculating Autocorrlation function and partil autocorlation function


```{r}
acf(EURGBPARIMATS,lag.max=34)
pacf(EURGBPARIMATS, lag.max = 34)
```


## Adjusting and ensuring there are no seasonality
```{r}
TSseasonallyadjustedEURGBP <- EURGBPARIMATS- ComponentEURGBP$seasonal 
StationaryEURGBP <- diff(TSseasonallyadjustedEURGBP, differences=1)
plot(StationaryEURGBP)
```


## Calculating again for ACF and PACF after finding stationality

```{r}
acf(StationaryEURGBP, lag.max=34)
pacf(StationaryEURGBP, lag.max=34)
```


# Fitting The ARIMA Model
## ARIMA fitting (1,1,0)

```{r}
fitArima1EURGBP <- arima(EURGBPARIMATS, order =  c(1,0,0), include.mean = TRUE)
fitArima1EURGBP
```


##Arima Fitting (0,1,0)

```{r}
fitArima2EURGBP <- arima(EURGBPARIMATS, order =  c(0,1,0), include.mean = TRUE)
fitArima2EURGBP
```

## Arima Fitting (2,1,1)

```{r}
fitArima3EURGBP <- arima(EURGBPARIMATS, order = c(2,1,1), include.mean = TRUE)
fitArima3EURGBP
```


##Fitting Arima (4,0,4)

```{r}
fitArima4EURGBP <- arima(EURGBPARIMATS, order = c(4,0,4), include.mean = TRUE)
fitArima4EURGBP
```


##Best possible model is selected by AIC scores of the models



```{r}
library(dLagM)
ARIMAModelSelectionEURGBP = AIC(fitArima1EURGBP,fitArima2EURGBP,fitArima3EURGBP,fitArima4EURGBP)
sortScore(ARIMAModelSelectionEURGBP, score ="aic")
```

### Base on the above the fitArima1CanJap is selected

##

```{r}
confint(fitArima4EURGBP)
```

## Runing code to obtain Box Test Rest

```{r}
acf(fitArima4EURGBP$residuals)
library(FitAR)
library(bestglm)
 Box.test(resid(fitArima4EURGBP),type="Ljung",lag=20,fitdf=1)

qqnorm(fitArima4EURGBP$residuals)
qqline(fitArima4EURGBP$residuals)
```


## Using Auto.arima to find the best model fit

```{r}
library(forecast)
auto.arima(EURGBPARIMATS, trace=TRUE)
```




## forecasting using  Best model: ARIMA(4,0,4)    

```{r}
forecastarimaEURGBP<- predict(fitArima4EURGBP,n.ahead = 100)
forecastarimaEURGBP
par(mfrow = c(1,1))
```



