---
title: "ARIMA EUR And USD"
author: "Jane"
date: "28/04/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---


# Forcasting Exchange Rate Using ARIMA Model for EUR And USD
## Reading EUR and USD Currency into r


```{r}
library(readr)
library(dplyr)
EURUSDARIMA<-  read.csv ("EURUSD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateEURUSD = ("CLOSE"))

  
head(EURUSDARIMA)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

EURUSDARIMA$Date <- lubridate::ymd(EURUSDARIMA$Date)
tail(EURUSDARIMA)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(EURUSDARIMA))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
EURUSDARIMATS<- ts(as.vector(EURUSDARIMA$Rate),  frequency = 314, start= c(2000,01,03))
plot.ts(EURUSDARIMATS)
title("Time Series plot of EURUSDTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```


## Finding the component of the Time Series

```{r}
ComponentEURUSDARIMA <- decompose(EURUSDARIMATS)
plot(ComponentEURUSDARIMA)
```

## To To achieve stationarity by differencing the data – compute the differences between consecutive observations

```{r}
library("fUnitRoots")
urkpssTest(EURUSDARIMATS, type = c("tau"), lags = c("short"),use.lag = NULL, doplot = TRUE)
EURUSDStationary= diff(EURUSDARIMATS, differences=1)
plot(EURUSDStationary)
```


## Calculating Autocorrlation function and partil autocorlation function


```{r}
acf(EURUSDARIMATS,lag.max=34)
pacf(EURUSDARIMATS, lag.max = 34)
```


## Adjusting and ensuring there are no seasonality
```{r}
TSseasonallyadjustedCanJap <- EURUSDARIMATS- ComponentEURUSDARIMA$seasonal 
StationaryEURUSD<- diff(TSseasonallyadjustedCanJap, differences=1)
plot(StationaryEURUSD)
```


## Calculating again for ACF and PACF after finding stationality

```{r}
acf(StationaryEURUSD, lag.max=34)
pacf(StationaryEURUSD, lag.max=34)
```


# Fitting The ARIMA Model
## ARIMA fitting (1,1,0)

```{r}
fitArima1EURUSD <- arima(EURUSDARIMATS, order =  c(1,1,0), include.mean = TRUE)
fitArima1EURUSD
```


##Arima Fitting (1,1,1)

```{r}
fitArima2EURUSD <- arima(EURUSDARIMATS, order =  c(1,1,1), include.mean = TRUE)
fitArima2EURUSD
```

## Arima Fitting (1,0,0)

```{r}
fitArima3EURUSD <- arima(EURUSDARIMATS, order = c(1,0,0), include.mean = TRUE)
fitArima3EURUSD
```


##Fitting Arima (0,1,3)

```{r}
fitArima4EURUSD <- arima(EURUSDARIMATS, order = c(2,2,2), include.mean = TRUE)
fitArima4EURUSD
```


##Best possible model is selected by AIC scores of the models



```{r}
library(dLagM)
ARIMAModelSelectionEURUSD = AIC(fitArima1EURUSD,fitArima2EURUSD,fitArima3EURUSD,fitArima4EURUSD)
sortScore(ARIMAModelSelectionEURUSD, score ="aic")
```

### Base on the above the fitArima1CanJap is selected

##

```{r}
confint(fitArima3EURUSD)
```

## Runing code to obtain Box Test Rest

```{r}
acf(fitArima3EURUSD$residuals)
library(FitAR)
library(bestglm)
 Box.test(resid(fitArima3EURUSD),type="Ljung",lag=20,fitdf=1)

qqnorm(fitArima3EURUSD$residuals)
qqline(fitArima3EURUSD$residuals)
```


## Using Auto.arima to find the best model fit

```{r}
library(forecast)
auto.arima(EURUSDARIMATS, trace=TRUE)
```




## forecasting using  Best model: ARIMA(1,1,0)    

```{r}
forecastarimaEURUSD<- predict(fitArima3EURUSD,n.ahead = 100)
forecastarimaEURUSD
par(mfrow = c(1,1))
```

