---
title: "Final Project R File"
author: "Jane"
date: "07/04/2021"
output:
  pdf_document: default
  html_document: default
---


# Forcasting Exchange Rate 

## Reading Canadian and Japanes Currency into r
```{r}
library(readr)
library(dplyr)
CanJapCurrency <- readxl::read_xlsx ("CADJPY_Candlestick_1_D_BID_01.01.2000-31.12.2020.xlsx")%>%
  select('Gmt time', Close)%>%
  rename(Date = ('Gmt time'), Rate = ("Close"))

head(CanJapCurrency)
```
   





## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

CanJapCurrency$Date <- lubridate::ymd(CanJapCurrency$Date)
head(CanJapCurrency)

```



##Converting to Time Series and Ploting a graph to view the dataset



```{r}
library(tseries)

TsCanJapCurrency = ts( CanJapCurrency$Rate, frequency =314, start = c(2000,01,03))

plot(TsCanJapCurrency)
```

## Finding the component of the Time Series

```{r}
ComponentCanJapCurrency <- decompose(TsCanJapCurrency)
plot(ComponentCanJapCurrency)
```

## To To achieve stationarity by differencing the data – compute the differences between consecutive observations

```{r}
library("fUnitRoots")
urkpssTest(TsCanJapCurrency, type = c("tau"), lags = c("short"),use.lag = NULL, doplot = TRUE)
CanJapStationary= diff(TsCanJapCurrency, differences=1)
plot(CanJapStationary)
```


## Calculating Autocorrlation function and partil autocorlation function


```{r}
acf(TsCanJapCurrency,lag.max=34)
pacf(TsCanJapCurrency, lag.max = 34)
```


## Adjusting and ensuring there are no seasonality
```{r}
TSseasonallyadjustedCanJap <- TsCanJapCurrency- ComponentCanJapCurrency$seasonal 
StationaryCanJap <- diff(TSseasonallyadjustedCanJap, differences=1)
plot(StationaryCanJap)
```


## Calculating again for ACF and PACF after finding stationality

```{r}
acf(StationaryCanJap, lag.max=34)
pacf(StationaryCanJap, lag.max=34)
```


# Fitting The ARIMA Model
## ARIMA fitting (1,1,0)

```{r}
fitArima1CanJap <- arima(TsCanJapCurrency, order =  c(1,1,0), include.mean = TRUE)
fitArima1CanJap
```


##Arima Fitting (1,1,1)

```{r}
fitArima2CanJap <- arima(TsCanJapCurrency, order =  c(3,0,1), include.mean = TRUE)
fitArima2CanJap
```

## Arima Fitting (2,1,1)

```{r}
fitArima3CanJap <- arima(TsCanJapCurrency, order = c(2,1,1), include.mean = TRUE)
fitArima3CanJap
```


##Fitting Arima (0,1,3)

```{r}
FitArima4CanJap <- arima(TsCanJapCurrency, order = c(0,1,3), include.mean = TRUE)
FitArima4CanJap
```


##Best possible model is selected by AIC scores of the models



```{r}
library(dLagM)
ARIMAModelSelection = AIC(fitArima1CanJap,fitArima2CanJap,fitArima3CanJap,FitArima4CanJap)
sortScore(ARIMAModelSelection, score ="aic")
```

### Base on the above the fitArima1CanJap is selected

##

```{r}
confint(fitArima2CanJap)
```

## Runing code to obtain Box Test Rest

```{r}
acf(fitArima2CanJap$residuals)
library(FitAR)
library(bestglm)
 Box.test(resid(fitArima2CanJap),type="Ljung",lag=20,fitdf=1)

qqnorm(fitArima2CanJap$residuals)
qqline(fitArima2CanJap$residuals)
```


## Using Auto.arima to find the best model fit

```{r}
library(forecast)
auto.arima(TsCanJapCurrency, trace=TRUE)
```




## forecasting using  Best model: ARIMA(1,1,0)    

```{r}
forecastarimaCanJa<- predict(fitArima2CanJap,n.ahead = 100)
forecastarimaCanJa
par(mfrow = c(1,1))
```

