---
title: "ARIMA USJap CurrencyRate"
author: "Jane"
date: "27/04/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Forcasting Exchange Rate Using GARCH Model for US Dollar and Japenese Yen

## Reading Canadian and Japanes Currency into r
```{r}
library(readr)
library(dplyr)
USJapCurrencyARIMA <-  read.csv ("USDJPY_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateUSJapan = ("CLOSE"))

  
head(USJapCurrencyARIMA)
```
   




## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

USJapCurrencyARIMA$Date <- lubridate::ymd(USJapCurrencyARIMA$Date)
head(USJapCurrencyARIMA)

```



##Checking for obvious errors
```{r}
#Checking for obvious errors
which(is.na(USJapCurrencyARIMA))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
USJapARIMATS<- ts(as.vector(USJapCurrencyARIMA$Rate),  frequency = 320, start= c(2000,01,03))
plot.ts(USJapARIMATS)
title("Time Series plot of USJapTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```

## Finding the component of the Time Series

```{r}
ComponentUSJapCurrency <- decompose(USJapARIMATS)
plot(ComponentUSJapCurrency)
```

## To To achieve stationarity by differencing the data – compute the differences between consecutive observations

```{r}
library("fUnitRoots")
urkpssTest(USJapARIMATS, type = c("tau"), lags = c("short"),use.lag = NULL, doplot = TRUE)
USJapStationary= diff(USJapARIMATS, differences=1)
plot(USJapStationary)
```


## Calculating Autocorrlation function and partil autocorlation function


```{r}
acf(USJapARIMATS,lag.max=34)
pacf(USJapARIMATS, lag.max = 34)
```


## Adjusting and ensuring there are no seasonality
```{r}
TSseasonallyadjustedUSJap <- USJapARIMATS- ComponentUSJapCurrency$seasonal 
StationaryUSJap <- diff(TSseasonallyadjustedUSJap, differences=1)
plot(StationaryUSJap)
```


## Calculating again for ACF and PACF after finding stationality

```{r}
acf(StationaryUSJap, lag.max=34)
pacf(StationaryUSJap, lag.max=34)
```


# Fitting The ARIMA Model
## ARIMA fitting (1,1,0)

```{r}
fitArima1USJap <- arima(USJapARIMATS, order =  c(0,1,0), include.mean = TRUE)
fitArima1USJap
```


##Arima Fitting (1,1,1)

```{r}
fitArima2USJap <- arima(USJapARIMATS, order =  c(1,1,1), include.mean = TRUE)
fitArima2USJap
```

## Arima Fitting (3,0,1)

```{r}
fitArima3USJap <- arima(USJapARIMATS, order = c(2,0,1), include.mean = TRUE)
fitArima3USJap
```


##Fitting Arima (0,1,3)

```{r}
FitArima4USJap <- arima(USJapARIMATS, order = c(0,1,3), include.mean = TRUE)
FitArima4USJap
```


##Best possible model is selected by AIC scores of the models



```{r}
library(dLagM)
ARIMAModelSelectionUSJAP = AIC(fitArima1USJap,fitArima2USJap,fitArima3USJap,FitArima4USJap)
sortScore(ARIMAModelSelectionUSJAP, score ="aic")
```

### Base on the above the fitArima1CanJap is selected

##

```{r}
confint(fitArima3USJap)
```

## Runing code to obtain Box Test Rest

```{r}
acf(fitArima3USJap$residuals)
library(FitAR)
library(bestglm)
 Box.test(resid(fitArima3USJap),type="Ljung",lag=20,fitdf=1)

qqnorm(fitArima3USJap$residuals)
qqline(fitArima3USJap$residuals)
```


## Using Auto.arima to find the best model fit

```{r}
library(forecast)
auto.arima(USJapARIMATS, trace=TRUE)
```




## forecasting using  Best model: ARIMA(2,0,3)    

```{r}
forecastarimaUSJa<- predict(fitArima3USJap,n.ahead = 100)
forecastarimaUSJa
par(mfrow = c(1,1))
```

