---
title: "ARIMA Model GBP And USD"
author: "Jane"
date: "28/04/2021"
output:
  pdf_document: default
  html_document: default
---


 Forcasting Exchange Rate Using ARIMA Model for Bristish Pound And US Dollar

## Reading GBP and USD Currency into r
```{r}
library(readr)
library(dplyr)
GBPUSDARIMA <-  read.csv ("GBPUSD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateGBPUSD = ("CLOSE"))

  
tail(GBPUSDARIMA)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

GBPUSDARIMA$Date <- lubridate::ymd(GBPUSDARIMA$Date)
head(GBPUSDARIMA)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(GBPUSDARIMA))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
GBPUSDARIMATS<- ts(as.vector(GBPUSDARIMA$Rate),  frequency = 320
                   , start= c(2000,01,03))
plot.ts(GBPUSDARIMATS)
title("Time Series plot of GBPUSDTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```





## Finding the component of the Time Series

```{r}
ComponentGBPUSD <- decompose(GBPUSDARIMATS)
plot(ComponentGBPUSD)
```

## To To achieve stationarity by differencing the data – compute the differences between consecutive observations

```{r}
library("fUnitRoots")
urkpssTest(GBPUSDARIMATS, type = c("tau"), lags = c("short"),use.lag = NULL, doplot = TRUE)
GBPUSDStationary= diff(GBPUSDARIMATS, differences=1)
plot(GBPUSDStationary)
```


## Calculating Autocorrlation function and partil autocorlation function


```{r}
acf(GBPUSDARIMATS,lag.max=34)
pacf(GBPUSDARIMATS, lag.max = 34)
```


## Adjusting and ensuring there are no seasonality
```{r}
TSseasonallyadjustedGBPUSD <- GBPUSDARIMATS- ComponentGBPUSD$seasonal 
StationaryGBPUSD <- diff(TSseasonallyadjustedGBPUSD, differences=1)
plot(StationaryGBPUSD)
```


## Calculating again for ACF and PACF after finding stationality

```{r}
acf(StationaryGBPUSD, lag.max=34)
pacf(StationaryGBPUSD, lag.max=34)
```


# Fitting The ARIMA Model
## ARIMA fitting (1,1,0)

```{r}
fitArima1GBPUSD <- arima(GBPUSDARIMATS, order =  c(1,0,0), include.mean = TRUE)
fitArima1GBPUSD
```





##Arima Fitting (2,2,2)

```{r}
fitArima2GBPUSD <- arima(GBPUSDARIMATS, order =  c(2,2,2), include.mean = TRUE)
fitArima2GBPUSD

```

## Arima Fitting (2,1,1)

```{r}
fitArima3GBPUSD <- arima(GBPUSDARIMATS, order = c(2,1,1), include.mean = TRUE)
fitArima3GBPUSD
```


##Fitting Arima (0,1,3)

```{r}
fitArima4GBPUSD <- arima(GBPUSDARIMATS, order = c(3,1,0), include.mean = TRUE)
fitArima4GBPUSD
```


##Best possible model is selected by AIC scores of the models



```{r}
library(dLagM)
ARIMAModelSelectionGBPUSD = AIC(fitArima1GBPUSD,fitArima2GBPUSD,fitArima3GBPUSD,fitArima4GBPUSD)
sortScore(ARIMAModelSelectionGBPUSD, score ="aic")
```

### Base on the above the fitArima2CanJap is selected

##

```{r}
confint(fitArima2GBPUSD)
```

## Runing code to obtain Box Test Rest

```{r}
acf(fitArima2GBPUSD$residuals)
library(FitAR)
library(bestglm)
 Box.test(resid(fitArima2GBPUSD),type="Ljung",lag=20,fitdf=1)

qqnorm(fitArima2GBPUSD$residuals)
qqline(fitArima2GBPUSD$residuals)
```


## Using Auto.arima to find the best model fit

```{r}
library(forecast)
auto.arima(GBPUSDARIMATS, trace=TRUE)
```





## forecasting using  Best model: ARIMA(0,1,0)    

```{r}
forecastarimaGBPUSD<- predict(fitArima2GBPUSD,n.ahead = 100)
forecastarimaGBPUSD
par(mfrow = c(1,1))
```



