---
title: "ARIMA Model USCanada"
author: "Jane"
date: "27/04/2021"
output:
  pdf_document: default
  html_document: default
---




# Forcasting Exchange Rate 

## Reading Canadian and Japanes Currency into r
```{r}
library(readr)
library(dplyr)
USDCADARIMA <-  read.csv ("USDCAD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateUSDCAD = ("CLOSE"))

  
tail(USDCADARIMA)
```
   





## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

USDCADARIMA$Date <- lubridate::ymd(USDCADARIMA$Date)
head(USDCADARIMA)

```



##Converting to Time Series and Ploting a graph to view the dataset



```{r}
library(tseries)

tsUSDCADARIMA = ts( USDCADARIMA$RateUSDCAD, frequency =319, start = c(2000,01,03))

plot(tsUSDCADARIMA)
title("Time Series plot of USDCADTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```

## Finding the component of the Time Series

```{r}
ComponentUSDCADARIMA<- decompose(tsUSDCADARIMA)
plot(ComponentUSDCADARIMA)
```

## To To achieve stationarity by differencing the data – compute the differences between consecutive observations

```{r}
library("fUnitRoots")
urkpssTest(tsUSDCADARIMA, type = c("tau"), lags = c("short"),use.lag = NULL, doplot = TRUE)
USDCADStationary= diff(tsUSDCADARIMA, differences=1)
plot(USDCADStationary)
```


## Calculating Autocorrlation function and partil autocorlation function


```{r}
acf(tsUSDCADARIMA,lag.max=34)
pacf(tsUSDCADARIMA, lag.max = 34)
```


## Adjusting and ensuring there are no seasonality
```{r}
TSseasonallyadjustedCanJap <- tsUSDCADARIMA- ComponentUSDCADARIMA$seasonal 
StationaryUSDCADARIMA <- diff(TSseasonallyadjustedCanJap, differences=1)
plot(StationaryUSDCADARIMA)
```


## Calculating again for ACF and PACF after finding stationality

```{r}
acf(StationaryUSDCADARIMA, lag.max=34)
pacf(StationaryUSDCADARIMA, lag.max=34)
```


# Fitting The ARIMA Model
## ARIMA fitting (1,0,0)

```{r}
fitArima1USDCAD <- arima(tsUSDCADARIMA, order =  c(1,0,0), include.mean = TRUE)
fitArima1USDCAD
```


##Arima Fitting (1,1,1)

```{r}
fitArima2USDCAD<- arima(tsUSDCADARIMA, order =  c(1,1,1), include.mean = TRUE)
fitArima2USDCAD
```

## Arima Fitting (2,1,1)

```{r}
fitArima3USDCAD <- arima(tsUSDCADARIMA, order = c(2,1,1), include.mean = TRUE)
fitArima3USDCAD
```


##Fitting Arima (0,1,3)

```{r}
FitArima4USDCAD <- arima(tsUSDCADARIMA, order = c(0,1,3), include.mean = TRUE)
FitArima4USDCAD
```


##Best possible model is selected by AIC scores of the models



```{r}
library(dLagM)
USDCADARIMAModelSelection = AIC(fitArima1USDCAD,fitArima2USDCAD,fitArima3USDCAD,FitArima4USDCAD)
sortScore(USDCADARIMAModelSelection, score ="aic")
```

### Base on the above the fitArima1CanJap is selected

##

```{r}
confint(fitArima1USDCAD)
```

## Runing code to obtain Box Test Rest

```{r}
acf(fitArima1USDCAD$residuals)
library(FitAR)
library(bestglm)
 Box.test(resid(fitArima1USDCAD),type="Ljung",lag=20,fitdf=1)

qqnorm(fitArima1USDCAD$residuals)
qqline(fitArima1USDCAD$residuals)
```


## Using Auto.arima to find the best model fit

```{r}
library(forecast)
auto.arima(TsCanJapCurrency, trace=TRUE)
```




## forecasting using  Best model: ARIMA(1,1,0)    

```{r}
forecastarimaUSDCAD<- predict(fitArima1USDCAD,n.ahead = 100)
forecastarimaUSDCAD
par(mfrow = c(1,1))
```







