---
title: "ARIMA Model EUR And JPY"
author: "Jane"
date: "29/04/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---






 # Forcasting Exchange Rate Using ARIMA Model for EUR And US Dollar

## Reading EUR and EUR Currency into r
```{r}
library(readr)
library(dplyr)
EURJPYARIMA <-  read.csv ("EURJPY_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateEURJPY = ("CLOSE"))

  
head(EURJPYARIMA)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

EURJPYARIMA$Date <- lubridate::ymd(EURJPYARIMA$Date)
head(EURJPYARIMA)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(EURJPYARIMA))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
EURJPYARIMATS<- ts(as.vector(EURJPYARIMA$Rate),  frequency = 320, start= c(2000,01,03))
plot.ts(EURJPYARIMATS)
title("Time Series plot of EURJPYTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```


## Finding the component of the Time Series

```{r}
ComponentEURJPY <- decompose(EURJPYARIMATS)
plot(ComponentEURJPY)
```

## To To achieve stationarity by differencing the data – compute the differences between consecutive observations

```{r}
library("fUnitRoots")
urkpssTest(EURJPYARIMATS, type = c("tau"), lags = c("short"),use.lag = NULL, doplot = TRUE)
EURJPYStationary= diff(EURJPYARIMATS, differences=1)
plot(EURJPYStationary)
```


## Calculating Autocorrlation function and partil autocorlation function


```{r}
acf(EURJPYARIMATS,lag.max=34)
pacf(EURJPYARIMATS, lag.max = 34)
```


## Adjusting and ensuring there are no seasonality
```{r}
TSseasonallyadjustedEURJPY <- EURJPYARIMATS- ComponentEURJPY$seasonal 
StationaryEURJPY <- diff(TSseasonallyadjustedEURJPY, differences=1)
plot(StationaryEURJPY)
```


## Calculating again for ACF and PACF after finding stationality

```{r}
acf(StationaryEURJPY, lag.max=34)
pacf(StationaryEURJPY, lag.max=34)
```


# Fitting The ARIMA Model
## ARIMA fitting (1,0,4)

```{r}
fitArima1EURJPY <- arima(EURJPYARIMATS, order =  c(1,0,4), include.mean = TRUE)
fitArima1EURJPY
```


##Arima Fitting (1,0,3)

```{r}
fitArima2EURJPY <- arima(EURJPYARIMATS, order =  c(1,0,3), include.mean = TRUE)
fitArima2EURJPY
```

## Arima Fitting (4,0,0)

```{r}
fitArima3EURJPY <- arima(EURJPYARIMATS, order = c(4,0,0), include.mean = TRUE)
fitArima3EURJPY
```


##Fitting Arima (2,0,4)

```{r}
fitArima4EURJPY <- arima(EURJPYARIMATS, order = c(2,0,4), include.mean = TRUE)
fitArima4EURJPY
```


##Best possible model is selected by AIC scores of the models



```{r}
library(dLagM)
ARIMAModelSelectionEURJPY = AIC(fitArima1EURJPY,fitArima2EURJPY,fitArima3EURJPY,fitArima4EURJPY)
sortScore(ARIMAModelSelectionEURJPY, score ="aic")
```

### Base on the above the fitArima1CanJap is selected

##

```{r}
confint(fitArima1EURJPY)
```

## Runing code to obtain Box Test Rest

```{r}
acf(fitArima1EURJPY$residuals)
library(FitAR)
library(bestglm)
 Box.test(resid(fitArima1EURJPY),type="Ljung",lag=20,fitdf=1)

qqnorm(fitArima1EURJPY$residuals)
qqline(fitArima1EURJPY$residuals)
```


## Using Auto.arima to find the best model fit

```{r}
library(forecast)
auto.arima(EURJPYARIMATS, trace=TRUE)
```




## forecasting using  Best model: ARIMA(0,1,0)    

```{r}
forecastarimaEURJPY<- predict(fitArima1EURJPY,n.ahead = 100)
forecastarimaEURJPY
par(mfrow = c(1,1))
```



