---
title: "ARIMA Model GBP And JPY"
author: "Jane"
date: "28/04/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```






# Forcasting Exchange Rate Using ARIMA Model for Bristish Pound And Japanese Yen

## Reading GBP and JPY Currency into r
```{r}
library(readr)
library(dplyr)
GBPJPYARIMA <-  read.csv ("GBPJPY_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateGBPJPY = ("CLOSE"))

  
head(GBPJPYARIMA)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

GBPJPYARIMA$Date <- lubridate::ymd(GBPJPYARIMA$Date)
head(GBPJPYARIMA)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(GBPJPYARIMA))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
GBPJPYARIMATS<- ts(as.vector(GBPJPYARIMA$Rate),  frequency = 320, start= c(2000,01,03))
plot.ts(GBPJPYARIMATS)
title("Time Series plot of GBPJPYTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```
## Finding the component of the Time Series

```{r}
ComponentGBPJPY <- decompose(GBPJPYARIMATS)
plot(ComponentGBPJPY)
```

## To To achieve stationarity by differencing the data – compute the differences between consecutive observations

```{r}
library("fUnitRoots")
urkpssTest(GBPJPYARIMATS, type = c("tau"), lags = c("short"),use.lag = NULL, doplot = TRUE)
GBPJPYStationary= diff(GBPJPYARIMATS, differences=1)
plot(GBPJPYStationary)
```


## Calculating Autocorrlation function and partil autocorlation function


```{r}
acf(GBPJPYARIMATS,lag.max=34)
pacf(GBPJPYARIMATS, lag.max = 34)
```


## Adjusting and ensuring there are no seasonality
```{r}
TSseasonallyadjustedGBPJPY <- GBPJPYARIMATS- ComponentGBPJPY$seasonal 
StationaryGBPJPY<- diff(TSseasonallyadjustedGBPJPY, differences=1)
plot(StationaryGBPJPY)
```


## Calculating again for ACF and PACF after finding stationality

```{r}
acf(StationaryGBPJPY, lag.max=34)
pacf(StationaryGBPJPY, lag.max=34)
```


# Fitting The ARIMA Model
## ARIMA fitting (1,1,0)

```{r}
fitArima1GBPJPY <- arima(GBPJPYARIMATS, order =  c(1,1,0), include.mean = TRUE)
fitArima1GBPJPY
```


##Arima Fitting (4,0,1)

```{r}
fitArima2GBPJPY <- arima(GBPJPYARIMATS, order =  c(4,0,1), include.mean = TRUE)
fitArima2GBPJPY
```

## Arima Fitting (2,1,1)

```{r}
fitArima3GBPJPY <- arima(GBPJPYARIMATS, order = c(2,1,1), include.mean = TRUE)
fitArima3GBPJPY
```


##Fitting Arima (2,1,0)

```{r}
fitArima4GBPJPY <- arima(GBPJPYARIMATS, order = c(2,1,0), include.mean = TRUE)
fitArima4GBPJPY
```


##Best possible model is selected by AIC scores of the models



```{r}
library(dLagM)
ARIMAModelSelectionGBPJPY = AIC(fitArima1GBPJPY,fitArima2GBPJPY,fitArima3GBPJPY,fitArima4GBPJPY)
sortScore(ARIMAModelSelectionGBPJPY, score ="aic")
```

### Base on the above the fitArima1CanJap is selected

##

```{r}
confint(fitArima2GBPJPY)
```

## Runing code to obtain Box Test Rest

```{r}
acf(fitArima2GBPJPY$residuals)
library(FitAR)
library(bestglm)
 Box.test(resid(fitArima2GBPJPY),type="Ljung",lag=20,fitdf=1)

qqnorm(fitArima2GBPJPY$residuals)
qqline(fitArima2GBPJPY$residuals)
```


## Using Auto.arima to find the best model fit

```{r}
library(forecast)
auto.arima(GBPJPYARIMATS, trace=TRUE)
```




## forecasting using  Best model: ARIMA(1,1,0)    

```{r}
forecastarimaGBPJPY<- predict(fitArima2GBPJPY,n.ahead = 100)
forecastarimaGBPJPY
par(mfrow = c(1,1))
```







