---
title: "ARIMA Model GBP And CAD"
author: "Jane"
date: "28/04/2021"
output:
  pdf_document: default
  html_document: default
---



# Forcasting Exchange Rate Using ARIMA Model for Bristish Pound And canadian Dollar

## Reading GBP and CAD Currency into r
```{r}
library(readr)
library(dplyr)
GBPCADARIMA <-  read.csv ("GBPCAD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateGBPCAD = ("CLOSE"))

  
head(GBPCADARIMA)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

GBPCADARIMA$Date <- lubridate::ymd(GBPCADARIMA$Date)
head(GBPCADARIMA)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(GBPCADARIMA))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
GBPCADARIMATS<- ts(as.vector(GBPCADARIMA$Rate),  frequency = 313, start= c(2000,01,03))
plot.ts(GBPCADARIMATS)
title("Time Series plot of GBPCADTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```


## Finding the component of the Time Series

```{r}
ComponentGBPCAD <- decompose(GBPCADARIMATS)
plot(ComponentGBPCAD)
```

## To To achieve stationarity by differencing the data – compute the differences between consecutive observations

```{r}
library("fUnitRoots")
urkpssTest(GBPCADARIMATS, type = c("tau"), lags = c("short"),use.lag = NULL, doplot = TRUE)
GBPCADStationary= diff(GBPCADARIMATS, differences=1)
plot(GBPCADStationary)
```


## Calculating Autocorrlation function and partil autocorlation function


```{r}
acf(GBPCADARIMATS,lag.max=34)
pacf(GBPCADARIMATS, lag.max = 34)
```


## Adjusting and ensuring there are no seasonality
```{r}
TSseasonallyadjustedGBPCAD <- GBPCADARIMATS- ComponentGBPCAD$seasonal 
StationaryGBPCAD<- diff(TSseasonallyadjustedGBPCAD, differences=1)
plot(StationaryGBPCAD)
```


## Calculating again for ACF and PACF after finding stationality

```{r}
acf(StationaryGBPCAD, lag.max=34)
pacf(StationaryGBPCAD, lag.max=34)
```


# Fitting The ARIMA Model
## ARIMA fitting (3,0,3)

```{r}
fitArima1GBPCAD <- arima(GBPCADARIMATS, order =  c(3,0,3), include.mean = TRUE)
fitArima1GBPCAD
```


##Arima Fitting (4,0,0)

```{r}
fitArima2GBPCAD <- arima(GBPCADARIMATS, order =  c(4,0,0), include.mean = TRUE)
fitArima2GBPCAD
```

## Arima Fitting (4,0,2)

```{r}
fitArima3GBPCAD <- arima(GBPCADARIMATS, order = c(4,0,2), include.mean = TRUE)
fitArima3GBPCAD
```


##Fitting Arima (0,1,3)

```{r}
fitArima4GBPCAD <- arima(GBPCADARIMATS, order = c(3,1,0), include.mean = TRUE)
fitArima4GBPCAD
```


##Best possible model is selected by AIC scores of the models



```{r}
library(dLagM)
ARIMAModelSelectionGBPCAD = AIC(fitArima1GBPCAD,fitArima2GBPCAD,fitArima3GBPCAD,fitArima4GBPCAD)
sortScore(ARIMAModelSelectionGBPCAD, score ="aic")
```

### Base on the above the fitArima1CanJap is selected

##

```{r}
confint(fitArima3GBPCAD)
```

## Runing code to obtain Box Test Rest

```{r}
acf(fitArima3GBPCAD$residuals)
library(FitAR)
library(bestglm)
 Box.test(resid(fitArima3GBPCAD),type="Ljung",lag=20,fitdf=1)

qqnorm(fitArima3GBPCAD$residuals)
qqline(fitArima3GBPCAD$residuals)
```


## Using Auto.arima to find the best model fit

```{r}
library(forecast)
auto.arima(GBPCADARIMATS, trace=TRUE)
```




## forecasting using  Best model: ARIMA(1,1,0)    

```{r}
forecastarimaGBPCAD<- predict(fitArima3GBPCAD,n.ahead = 100)
forecastarimaGBPCAD
par(mfrow = c(1,1))
```



