---
title: "ARIMA Model EUR And CAD"
author: "Jane"
date: "01/05/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---



# Forcasting Exchange Rate Using ARIMA Model for EUR And CAD
## Reading EUR and CAD Currency into r



```{r}
library(readr)
library(dplyr)
EURCADARIMA<-  read.csv ("EURCAD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateEURCAD = ("CLOSE"))

  
head(EURCADARIMA)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

EURCADARIMA$Date <- lubridate::ymd(EURCADARIMA$Date)
head(EURCADARIMA)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(EURCADARIMA))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
EURCADARIMATS<- ts(as.vector(EURCADARIMA$Rate),  frequency = 322, start= c(2000,01,03))
plot.ts(EURCADARIMATS)
title("Time Series plot of EURCADTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```




## Finding the component of the Time Series

```{r}
ComponentEURCAD <- decompose(EURCADARIMATS)
plot(ComponentEURCAD)
```

## To To achieve stationarity by differencing the data – compute the differences between consecutive observations

```{r}
library("fUnitRoots")
urkpssTest(EURCADARIMATS, type = c("tau"), lags = c("short"),use.lag = NULL, doplot = TRUE)
EURCADStationary= diff(EURCADARIMATS, differences=1)
plot(EURCADStationary)
```


## Calculating Autocorrlation function and partil autocorlation function


```{r}
acf(EURCADARIMATS,lag.max=34)
pacf(EURCADARIMATS, lag.max = 34)
```


## Adjusting and ensuring there are no seasonality
```{r}
TSseasonallyadjustedEURCAD <- EURCADARIMATS- ComponentEURCAD$seasonal 
StationaryEURCAD <- diff(TSseasonallyadjustedEURCAD, differences=1)
plot(StationaryEURCAD)
```


## Calculating again for ACF and PACF after finding stationality

```{r}
acf(StationaryEURCAD, lag.max=34)
pacf(StationaryEURCAD, lag.max=34)
```


# Fitting The ARIMA Model
## ARIMA fitting (1,1,0)

```{r}
fitArima1EURCAD <- arima(EURCADARIMATS, order =  c(1,0,0), include.mean = TRUE)
fitArima1EURCAD
```


##Arima Fitting (1,0,1)

```{r}
fitArima2EURCAD <- arima(EURCADARIMATS, order =  c(1,0,1), include.mean = TRUE)
fitArima2EURCAD
```

## Arima Fitting (2,1,1)

```{r}
fitArima3EURCAD <- arima(EURCADARIMATS, order = c(2,1,1), include.mean = TRUE)
fitArima3EURCAD
```


##Fitting Arima (3,1,0)

```{r}
fitArima4EURCAD <- arima(EURCADARIMATS, order = c(3,1,0), include.mean = TRUE)
fitArima4EURCAD
```


##Best possible model is selected by AIC scores of the models



```{r}
library(dLagM)
ARIMAModelSelectionEURCAD = AIC(fitArima1EURCAD,fitArima2EURCAD,fitArima3EURCAD,fitArima4EURCAD)
sortScore(ARIMAModelSelectionEURCAD, score ="aic")
```

### Base on the above the fitArima1CanJap is selected

##

```{r}
confint(fitArima2EURCAD)
```

## Runing code to obtain Box Test Rest

```{r}
acf(fitArima2EURCAD$residuals)
library(FitAR)
library(bestglm)
 Box.test(resid(fitArima2EURCAD),type="Ljung",lag=20,fitdf=1)

qqnorm(fitArima2EURCAD$residuals)
qqline(fitArima2EURCAD$residuals)
```


## Using Auto.arima to find the best model fit

```{r}
library(forecast)
auto.arima(EURCADARIMATS, trace=TRUE)
```




## forecasting using  Best model: ARIMA(0,1,0)    

```{r}
forecastarimaEURCAD<- predict(fitArima2EURCAD,n.ahead = 100)
forecastarimaEURCAD
par(mfrow = c(1,1))
```



