---
title: "DCC Model EUR And CAD"
author: "Jane"
date: "01/05/2021"
output: html_document
---


# Forcasting Exchange Rate Using DCC GARCH Model for EUR And CAD pair and GBP CAD
## Reading EUR and CAD Currency into r


```{r}
library(readr)
library(dplyr)
EURCADDCCGARCH<-  read.csv ("EURCAD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date1 = ('GMT.TIME'), RateEURCAD = ("CLOSE"))%>%
  slice(1:6261)
  
tail(EURCADDCCGARCH)
```



## Reading GBP and CAD Currency into r
```{r}
library(readr)
library(dplyr)
GBPCADdccGARCH <-  read.csv ("GBPCAD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateGBPCAD = ("CLOSE"))

  
tail(GBPCADdccGARCH)
```

## Combining both Data Set

```{r}
DCCEURCADnGBPCAD <- cbind(GBPCADdccGARCH, EURCADDCCGARCH)

head (DCCEURCADnGBPCAD)
```

## Selecting Date and the two pair of currency

```{r}
DCCECGC <- select(DCCEURCADnGBPCAD, Date, RateGBPCAD, RateEURCAD)
head(DCCECGC)
```




## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)
DCCECGC$Date <- lubridate::ymd(DCCECGC$Date)
head(DCCECGC)

```


##Checking for obvious errors 

```{r}
#Checking for obvious errors
which(is.na(DCCECGC))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
RateGBPCADTS<- ts(DCCECGC$RateGBPCAD,    frequency = 314, start= c(2000,01,03))
RateEURCADTS <- ts(DCCECGC$RateEURCAD, frequency = 314, start = c(2000,01,03))
GBPCADEURCADTSDCC <- cbind(RateEURCADTS, RateGBPCADTS)
plot.ts(GBPCADEURCADTSDCC)
title("Time Series plot of GBPCADnEURCADTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```





## 
```{r}



GBPCADEURCADLogTranDCC<-log(GBPCADEURCADTSDCC)

ar(GBPCADEURCADLogTranDCC)
```




## Differencing the time series

```{r}
DiffGBPCADEURCAD<-diff(GBPCADEURCADLogTranDCC) 
ar(DiffGBPCADEURCAD)
plot(DiffGBPCADEURCAD)
```




## Defining the the model


```{r}
library(rmgarch)  


ugarch_spec1 <- ugarchspec(mean.model = list(armaOrder = c(0,0), include.mean = FALSE), 
                          variance.model = list(model = "sGARCH", garchOrder = c(1,1)))

ugarch_spec2 <- ugarchspec(mean.model = list(armaOrder = c(1,0), include.mean = FALSE), 
                          variance.model = list(model = "sGARCH", garchOrder = c(1,1)))
ugarch_spec3 <- ugarchspec(mean.model = list(armaOrder = c(2,0), include.mean = FALSE), 
                          variance.model = list(model = "sGARCH", garchOrder = c(1,1)))

ugarch_spec <- c(ugarch_spec1,ugarch_spec2,ugarch_spec3)


# specify DCC model
dcc_spec <- dccspec(uspec = multispec(replicate(ugarch_spec1, n = 2)),
                    VAR = TRUE, lag = 3,
                    model = "DCC", dccOrder = c(1,1))

```


```{r}
library(rmgarch)  

# specify i.i.d. model for the univariate time series
ugarch_spec <- ugarchspec(mean.model = list(armaOrder = c(0,0), include.mean = FALSE), 
                          variance.model = list(model = "sGARCH", garchOrder = c(1,1)))

# specify DCC model
dcc_spec <- dccspec(uspec = multispec(replicate(ugarch_spec, n = 2)),
                    VAR = TRUE, lag = 3,
                    model = "DCC", dccOrder = c(1,1))
```




## Next, we fit the model:

fit1 = dccfit(spec1, data = Dat, fit.control = list(eval.se = TRUE), fit = multf, cluster = cl)
fit1a = dccfit(spec1a, data = Dat, fit.control = list(eval.se = TRUE), fit = multf, cluster = cl)
fit2 = dccfit(spec2, data = Dat, fit.control = list(eval.se = TRUE), fit = multf, cluster = cl)
fit2a = dccfit(spec2a, data = Dat, fit.control = list(eval.se = TRUE), fit = multf, cluster = cl)


```{r}

# estimate model
garchdcc_fitEURCADGBPCAD <- dccfit(dcc_spec, data = DiffGBPCADEURCAD, solver = "nlminb")
garchdcc_fitEURCADGBPCAD
```


```{r}
plot(garchdcc_fitEURCADGBPCAD)
```




## Forecasting 


```{r}
ForecastDCCEURCADGBPCAD = dccforecast(garchdcc_fitEURCADGBPCAD, n.ahead = 100, n.roll = 0)
ForecastDCCEURCADGBPCAD
```


```{r}
H1 = rcov(forc2)
	
cat("\nDCC Forecast Summary:\n")
(forc2)

cat("\nRolling and mixed Rolling Forecast DCC model Conditional Covariance check:\n")
cat("\nFirst:\n")
print( H1[[1]][,,1] )
cat("\n100:\n")
```




```{r}
# extract time-varying covariance and correlation matrix
dcc_cor <- rcor(garchdcc_fit)
dim(dcc_cor)
#> [1]    3    3 1007

#plot
corr_t <- xts(cbind(dcc_cor[1, 2, ], dcc_cor[1, 3, ], dcc_cor[2, 3, ]), order.by = index(logreturns))
colnames(corr_t) <- c("SPY vs LTL", "SPY vs IEF", "TLT vs IEF")
plot(corr_t, col = c("black", "red", "blue"),
     main = "Time-varying correlations", legend.loc = "left")
```


