---
title: "DCCGARCH Model EURJPY GBPJPY"
author: "Jane"
date: "02/05/2021"
output: html_document
---






# Forcasting Exchange Rate Using DCC GARCH Model for EUR And JPY pair and GBP USD
## Reading EUR and JPY Currency into r


```{r}
library(readr)
library(dplyr)
EURJPYDCCGARCH<-  read.csv ("EURJPY_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date1 = ('GMT.TIME'), RateEURJPY = ("CLOSE"))
 
  
tail(EURJPYDCCGARCH)
```



## Reading GBP and USD Currency into r
```{r}
library(readr)
library(dplyr)
GBPJPYdccGARCH <-  read.csv ("GBPUSD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateGBPJPY = ("CLOSE"))
  
tail(GBPJPYdccGARCH)
```

## Combining both Data Set

```{r}
DCCEURJPYnGBPJPY <- cbind(GBPJPYdccGARCH, EURJPYDCCGARCH)

head (DCCEURJPYnGBPJPY)
```

## Selecting Date and the two pair of currency

```{r}
DCCEURnGBPJPY <- select(DCCEURJPYnGBPJPY, Date, RateGBPJPY, RateEURJPY)
head(DCCEURnGBPJPY)
```




## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)
DCCEURnGBPJPY$Date <- lubridate::ymd(DCCEURnGBPJPY$Date)
head(DCCEURnGBPJPY)

```


##Checking for obvious errors 

```{r}
#Checking for obvious errors
which(is.na(DCCEURnGBPJPY))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
RateGBPJPYTS<- ts(DCCEURnGBPJPY$RateGBPJPY,    frequency = 320, start= c(2000,01,03))
RateEURJPYTS <- ts(DCCEURnGBPJPY$RateEURJPY, frequency = 320, start = c(2000,01,03))
GBPJPYEURJPYTSDCC <- cbind(RateEURJPYTS, RateGBPJPYTS)
plot.ts(GBPJPYEURJPYTSDCC)
title("Time Series plot of GBPJPYnEURJPYTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```





## 
```{r}



GBPJPYEURJPYLogTranDCC<-log(GBPJPYEURJPYTSDCC)

ar(GBPJPYEURJPYLogTranDCC)
```




## Differencing the time series

```{r}
DiffGBPJPYEURJPY<-diff(GBPJPYEURJPYLogTranDCC) 
ar(DiffGBPJPYEURJPY)
plot(DiffGBPJPYEURJPY)
```




## Defining the the model


```{r}
library(rmgarch)  


ugarch_spec1 <- ugarchspec(mean.model = list(armaOrder = c(0,0), include.mean = FALSE), 
                          variance.model = list(model = "sGARCH", garchOrder = c(1,1)))

ugarch_spec2 <- ugarchspec(mean.model = list(armaOrder = c(1,0), include.mean = FALSE), 
                          variance.model = list(model = "sGARCH", garchOrder = c(1,1)))
ugarch_spec3 <- ugarchspec(mean.model = list(armaOrder = c(2,0), include.mean = FALSE), 
                          variance.model = list(model = "sGARCH", garchOrder = c(1,1)))

ugarch_spec <- c(ugarch_spec1,ugarch_spec2,ugarch_spec3)


# specify DCC model
dcc_spec <- dccspec(uspec = multispec(replicate(ugarch_spec1, n = 2)),
                    VAR = TRUE, lag = 3,
                    model = "DCC", dccOrder = c(1,1))

```


```{r}
library(rmgarch)  

# specify i.i.d. model for the univariate time series
ugarch_spec <- ugarchspec(mean.model = list(armaOrder = c(0,0), include.mean = FALSE), 
                          variance.model = list(model = "sGARCH", garchOrder = c(1,1)))

# specify DCC model
dcc_spec <- dccspec(uspec = multispec(replicate(ugarch_spec, n = 2)),
                    VAR = TRUE, lag = 3,
                    model = "DCC", dccOrder = c(1,1))
```





```{r}

# estimate model
garchdcc_fitEURJPYGBPJPY <- dccfit(dcc_spec, data = DiffGBPJPYEURJPY, solver = "nlminb")
garchdcc_fitEURJPYGBPJPY
```


```{r}
plot(garchdcc_fitEURJPYGBPJPY)
```




## Forecasting 


```{r}
ForecastDCCEURJPYGBPJPY = dccforecast(garchdcc_fitEURJPYGBPJPY, n.ahead = 100, n.roll = 0)
ForecastDCCEURJPYGBPJPY
```


```{r}
H1 = rcov(forc2)
	
cat("\nDCC Forecast Summary:\n")
(forc2)

cat("\nRolling and mixed Rolling Forecast DCC model Conditional Covariance check:\n")
cat("\nFirst:\n")
print( H1[[1]][,,1] )
cat("\n100:\n")
```




```{r}
# extract time-varying covariance and correlation matrix
dcc_cor <- rcor(garchdcc_fit)
dim(dcc_cor)
#> [1]    3    3 1007

#plot
corr_t <- xts(cbind(dcc_cor[1, 2, ], dcc_cor[1, 3, ], dcc_cor[2, 3, ]), order.by = index(logreturns))
colnames(corr_t) <- c("SPY vs LTL", "SPY vs IEF", "TLT vs IEF")
plot(corr_t, col = c("black", "red", "blue"),
     main = "Time-varying correlations", legend.loc = "left")
```


