---
title: "DCCGARCH Model EURUSD GBPUSD"
author: "Jane"
date: "02/05/2021"
output: html_document
---




# Forcasting Exchange Rate Using DCC GARCH Model for EUR And USD pair and GBP USD
## Reading EUR and USD Currency into r


```{r}
library(readr)
library(dplyr)
EURUSDDCCGARCH<-  read.csv ("EURUSD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date1 = ('GMT.TIME'), RateEURUSD = ("CLOSE"))%>%
  slice(1:6399)
  
  
tail(EURUSDDCCGARCH)
```



## Reading GBP and USD Currency into r
```{r}
library(readr)
library(dplyr)
GBPUSDdccGARCH <-  read.csv ("GBPUSD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateGBPUSD = ("CLOSE"))
  
tail(GBPUSDdccGARCH)
```

## Combining both Data Set

```{r}
DCCEURUSDnGBPUSD <- cbind(GBPUSDdccGARCH, EURUSDDCCGARCH)

head (DCCEURUSDnGBPUSD)
```

## Selecting Date and the two pair of currency

```{r}
DCCEURnGBPUSD <- select(DCCEURUSDnGBPUSD, Date, RateGBPUSD, RateEURUSD)
head(DCCEURnGBPUSD)
```




## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)
DCCEURnGBPUSD$Date <- lubridate::ymd(DCCEURnGBPUSD$Date)
head(DCCEURnGBPUSD)

```


##Checking for obvious errors 

```{r}
#Checking for obvious errors
which(is.na(DCCEURnGBPUSD))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
RateGBPUSDTS<- ts(DCCEURnGBPUSD$RateGBPUSD,    frequency = 314, start= c(2000,01,03))
RateEURUSDTS <- ts(DCCEURnGBPUSD$RateEURUSD, frequency = 314, start = c(2000,01,03))
GBPUSDEURUSDTSDCC <- cbind(RateEURUSDTS, RateGBPUSDTS)
plot.ts(GBPUSDEURUSDTSDCC)
title("Time Series plot of GBPUSDnEURUSDTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```





## 
```{r}



GBPUSDEURUSDLogTranDCC<-log(GBPUSDEURUSDTSDCC)

ar(GBPUSDEURUSDLogTranDCC)
```




## Differencing the time series

```{r}
DiffGBPUSDEURUSD<-diff(GBPUSDEURUSDLogTranDCC) 
ar(DiffGBPUSDEURUSD)
plot(DiffGBPUSDEURUSD)
```




## Defining the the model


```{r}
library(rmgarch)  


ugarch_spec1 <- ugarchspec(mean.model = list(armaOrder = c(0,0), include.mean = FALSE), 
                          variance.model = list(model = "sGARCH", garchOrder = c(1,1)))

ugarch_spec2 <- ugarchspec(mean.model = list(armaOrder = c(1,0), include.mean = FALSE), 
                          variance.model = list(model = "sGARCH", garchOrder = c(1,1)))
ugarch_spec3 <- ugarchspec(mean.model = list(armaOrder = c(2,0), include.mean = FALSE), 
                          variance.model = list(model = "sGARCH", garchOrder = c(1,1)))

ugarch_spec <- c(ugarch_spec1,ugarch_spec2,ugarch_spec3)


# specify DCC model
dcc_spec <- dccspec(uspec = multispec(replicate(ugarch_spec1, n = 2)),
                    VAR = TRUE, lag = 3,
                    model = "DCC", dccOrder = c(1,1))

```


```{r}
library(rmgarch)  

# specify i.i.d. model for the univariate time series
ugarch_spec <- ugarchspec(mean.model = list(armaOrder = c(0,0), include.mean = FALSE), 
                          variance.model = list(model = "sGARCH", garchOrder = c(1,1)))

# specify DCC model
dcc_spec <- dccspec(uspec = multispec(replicate(ugarch_spec, n = 2)),
                    VAR = TRUE, lag = 3,
                    model = "DCC", dccOrder = c(1,1))
```




## Next, we fit the model:

fit1 = dccfit(spec1, data = Dat, fit.control = list(eval.se = TRUE), fit = multf, cluster = cl)
fit1a = dccfit(spec1a, data = Dat, fit.control = list(eval.se = TRUE), fit = multf, cluster = cl)
fit2 = dccfit(spec2, data = Dat, fit.control = list(eval.se = TRUE), fit = multf, cluster = cl)
fit2a = dccfit(spec2a, data = Dat, fit.control = list(eval.se = TRUE), fit = multf, cluster = cl)


```{r}

# estimate model
garchdcc_fitEURUSDGBPUSD <- dccfit(dcc_spec, data = DiffGBPUSDEURUSD, solver = "nlminb")
garchdcc_fitEURUSDGBPUSD
```


```{r}
plot(garchdcc_fitEURCADGBPCAD)
```




## Forecasting 


```{r}
ForecastDCCEURUSDGBPUSD = dccforecast(garchdcc_fitEURUSDGBPUSD, n.ahead = 100, n.roll = 0)
ForecastDCCEURUSDGBPUSD
```


```{r}
H1 = rcov(forc2)
	
cat("\nDCC Forecast Summary:\n")
(forc2)

cat("\nRolling and mixed Rolling Forecast DCC model Conditional Covariance check:\n")
cat("\nFirst:\n")
print( H1[[1]][,,1] )
cat("\n100:\n")
```




```{r}
# extract time-varying covariance and correlation matrix
dcc_cor <- rcor(garchdcc_fit)
dim(dcc_cor)
#> [1]    3    3 1007

#plot
corr_t <- xts(cbind(dcc_cor[1, 2, ], dcc_cor[1, 3, ], dcc_cor[2, 3, ]), order.by = index(logreturns))
colnames(corr_t) <- c("SPY vs LTL", "SPY vs IEF", "TLT vs IEF")
plot(corr_t, col = c("black", "red", "blue"),
     main = "Time-varying correlations", legend.loc = "left")
```


