---
title: "Fuzzuy ARIMA"
author: "Jane"
date: "21/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#  Forecasting Using Fuzzy ARIMA Model

## Reading Canadian and Japanes Currency into r
```{r}
library(readr)
library(dplyr)
CanadianJapanCurrencyFuzzy<- readxl::read_xlsx ("CADJPY_Candlestick_1_D_BID_01.01.2000-31.12.2020.xlsx")%>%
  select('Gmt time', Close)%>%
  rename(Date = ('Gmt time'), Rate = ("Close"))

head(CanadianJapanCurrencyFuzzy)
```



## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)
CanadianJapanCurrencyFuzzy$Date <- lubridate::ymd(CanadianJapanCurrencyFuzzy$Date)
head(CanadianJapanCurrencyFuzzy)

```

##Checking for obvious errors 

```{r}
#Checking for obvious errors
which(is.na(CanadianJapanCurrencyFuzzy))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
CanjapTSFuzzy<- ts(as.vector(CanadianJapanCurrencyFuzzy$Rate),  frequency = 314, start= c(2000,01,03))
plot.ts(CanjapTSFuzzy)
title("Time Series plot of CanJapTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```



## Forecaste of Canadian Dollar and Japanese Yen using Fuzzy Arima


```{r}
par(mfrow=c(2,2))

fuzzy.ts1(CanjapTSFuzzy,n=100,type="Singh",plot=TRUE)
```

#Abbasov Mamedova model
fuzzy.ts2(enrollment,n=5,w=5,C=0.01,forecast=5,plot=TRUE,type="Abbasov-Mamedova")

#NFTS model
fuzzy.ts2(enrollment,n=5,w=5,C=0.01,forecast=5,plot=TRUE,type="NFTS")
```
```


par(mfrow=c(1,2))







