---
title: "GARCH Model EUR And USD"
author: "Jane"
date: "28/04/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---





# Forcasting Exchange Rate Using GARCH Model for EUR And USD
## Reading EUR and USD Currency into r


```{r}
library(readr)
library(dplyr)
EURUSDGARCH<-  read.csv ("EURUSD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateEURUSD = ("CLOSE"))

  
head(EURUSDGARCH)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

EURUSDGARCH$Date <- lubridate::ymd(EURUSDGARCH$Date)
head(EURUSDGARCH)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(EURUSDGARCH))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
EURUSDGARCHTS<- ts(as.vector(EURUSDGARCH$Rate),  frequency = 322, start= c(2000,01,03))
plot.ts(EURUSDGARCHTS)
title("Time Series plot of EURUSDTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```








##Dealing with Conditional Heteroscedaticity:


```{r}
 
DifflogEURUSDGarch= diff(log(EURUSDGARCHTS))*100
plot(DifflogEURUSDGarch)
title("Plot of returns of EURUSD", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```

##nature as almost at all lags the p-values fall below the significance levels.



```{r}
library(TSA)
McLeod.Li.test(y= DifflogEURUSDGarch,main="McLeod-Li test statistics for Daily return series")
```



## In order to get an order of GARCH , we further transform the return series into absolute values and squared return values.


```{r}

abs = abs(DifflogEURUSDGarch)
sqr = DifflogEURUSDGarch^2
```




# GARCH Model specification:

```{r}
par(mfrow=c(1,2))
acf(abs, ci.type="ma",main=" ACF for abs. returns")
pacf(abs, main=" PACF plot for abs.returns")
```


##From ACF and PACF we see many lags are significant. Hence, we plot EACF to get the candidate models

```{r}
eacf(abs) 
```

##From the squared returns ACF and PACF plot
```{r}


par(mfrow=c(1,2))
acf(sqr, ci.type="ma",main="ACF  for sqr. return")
pacf(sqr, main="PACF for sqr. return")
```

##

```{r}
eacf(sqr) 
```



### With reference to the Dickey-Fuller Test, p-value is less than the 0.02 and we can reject the null hypothesis stating the non-stationarity. Hence , we can proceed further for model selection .


#MODEL ESTIMATION:
##GARCH (2,1): for GBP and USD Curruency Pair


```{r}


# GARCH(2,1)
library(tseries)
EURUSDGARCHFit.21 = garch(DifflogEURUSDGarch,order=c(2,1),trace =FALSE)
summary(EURUSDGARCHFit.21)
```



## GARCH (2,2):
##This model can be interpreted as an overfit model of GARCH(2,1) and p values from residual tests confirms that residuals ahas a low correlated. Thus this model is may consider to be a good fit.

```{r}

EURUSDGARCHFit.22 = garch(DifflogEURUSDGarch, order =c(2,2),trace =FALSE)
summary(EURUSDGARCHFit.22)
```


##GARCH (3,1):
##This model can be interpreted as an overfit model of GARCH(2,1) and GARCH (2,2). This model may not be consider to be a good fit.



```{r}

EURUSDGARCHFit.31 = garch(DifflogEURUSDGarch,order=c(3,1),trace =FALSE)
summary(EURUSDGARCHFit.31)
```


##GARCH (1,1):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are lowly  correlated. Thus this model is may consider to be a good fit.

# GARCH(1,1) 

```{r}
EURUSDGARCHFit.11 = garch(DifflogEURUSDGarch,order=c(1,1),trace =FALSE)
summary(EURUSDGARCHFit.11)
```


## GARCH (3,3):
This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are lowly correlated. Thus, this model is may consider to be a good fit.

# GARCH(3,3)

```{r}

EURUSDGARCHFit.33 = garch(DifflogEURUSDGarch,order=c(3,3),trace =FALSE)
summary(EURUSDGARCHFit.33)
```


##GARCH (4,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are lowly correlated. Thus, this model is may considered to be a good fit.



```{r}

EURUSDGARCHFit.42 = garch(DifflogEURUSDGarch,order=c(4,2),trace =FALSE)
summary(EURUSDGARCHFit.42)
```
  ##
  
```{r}

EURUSDGARCHFit.41 = garch(DifflogEURUSDGarch,order=c(4,1),trace =FALSE)
summary(EURUSDGARCHFit.41)
```


# Model Selection:
##Best possible model is selected by AIC scores of the models. From the below sort function, GARCH(1,1) would be the best model for the return series. From the p-value, 3.1 also has the lowest correlation


```{r}
library(dLagM)
GARCHModelSelectionEURUSD = AIC(EURUSDGARCHFit.21,EURUSDGARCHFit.22 ,EURUSDGARCHFit.31,EURUSDGARCHFit.11,EURUSDGARCHFit.33, EURUSDGARCHFit.42, EURUSDGARCHFit.41)
sortScore(GARCHModelSelectionEURUSD, score ="aic")
```


# Model Fitting:

```{r}
library(rugarch)
EURUSDmodel1.1<-ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1,1)), 
                  mean.model = list(armaOrder = c(5,6), include.mean = TRUE), 
                  distribution.model = "norm")
                  
EURUSDgarchMODEL1.1<-ugarchfit(spec=EURUSDmodel1.1,data=DifflogEURUSDGarch, out.sample = 100)
plot(EURUSDgarchMODEL1.1,which="all")
```

##Model Diagnostics

```{r}
EURUSDgarchMODEL1.1
```


## Forecasting

```{r}
forcgarchEURUSD= ugarchforecast(EURUSDgarchMODEL1.1, data = DiffEURUSDLogTran, n.ahead = 100)
print(forcgarchEURUSD)
```




## Forecasting the rate


```{r}
p.t_1 = 1.22141
  R_t <- c( -0.0275978, 0.0361291, 0.0437004, -0.0135389, -0.0097401, 0.0491042, 0.0190393, -0.0249553, 0.0152887,
0.0458895, -0.0068181, -0.0173138, 0.0354398, 0.0279638, -0.0223030, 0.0026319, 0.0417460, 0.0040521, -0.0218048 , 
0.0237713, 0.0324900, -0.0149448, -0.0075291, 0.0359013, 0.0132500, -0.0213035, 0.0123405, 0.0341422, -0.0064029, -0.0137396, 0.0279872, 0.0205280, -0.0176802, 0.0026417, 0.0325842, 0.0023186, -0.0164933, 0.0193136,  0.0250729, -0.0118682, -0.0048218, 0.0285477, 0.0100287, -0.0161260, 0.0108214, 0.0268314, -0.0050161, -0.0096628, 0.0228224, 
0.0160137, -0.0133096, 0.0033744, 0.0260387, 0.0018955, -0.0118673, 0.0163022, 0.0198713, -0.0088247, -0.0024321, 
0.0232014, 0.0080563, -0.0116901, 0.0098147, 0.0215244, -0.0034920, -0.0062746, 0.0189684, 0.0128947, -0.0095976,
0.0040475, 0.0211588, 0.0019286, -0.0080979, 0.0140349, 0.0160921, -0.0061787, -0.0005080, 0.0191560,  0.0068066 , 
-0.0080744, 0.0090546, 0.0175720, -0.0020600, -0.0035774, 0.0160143, 0.0106873, -0.0065463, 0.0045738, 0.0174642,
0.0021690, -0.0050958, 0.0122724, 0.0133094, -0.0039585, 0.0009895, 0.0160534, 0.0060132, -0.0051789, 
0.0084419, 0.0145989 







)
  p_t= 0
  for (i in 1:100){
    p_t =  p.t_1  *((2.71828)^(R_t[i]/100))
   print(p_t)
    p.t_1=p_t
  }
  
```









