---
title: "GARCH Model GBP And CAD"
author: "Jane"
date: "28/04/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Forcasting Exchange Rate Using GARCH Model for Bristish Pound And canadian Dollar

## Reading GBP and CAD Currency into r
```{r}
library(readr)
library(dplyr)
GBPCADGARCH <-  read.csv ("GBPCAD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateGBPCAD = ("CLOSE"))

  
head(GBPCADGARCH)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

GBPCADGARCH$Date <- lubridate::ymd(GBPCADGARCH$Date)
head(GBPCADGARCH)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(GBPCADGARCH))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
GBPCADGARCHTS<- ts(as.vector(GBPCADGARCH$Rate),  frequency = 314, start= c(2000,01,03))
plot.ts(GBPCADGARCHTS)
title("Time Series plot of GBPCADTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```








##Dealing with Conditional Heteroscedaticity:


```{r}
 
DifflogGBPCADGarch= diff(log(GBPCADGARCHTS))*100
plot(DifflogGBPCADGarch)
title("Plot of returns of GBPCAD", sub = "(2013-2018)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```

##nature as almost at all lags the p-values fall below the significance levels.



```{r}
library(TSA)
McLeod.Li.test(y= DifflogGBPCADGarch,main="McLeod-Li test statistics for Daily return series")
```



## In order to get an order of GARCH , we further transform the return series into absolute values and squared return values.


```{r}

abs = abs(DifflogGBPCADGarch)
sqr = DifflogGBPCADGarch^2
```




# GARCH Model specification:

```{r}
par(mfrow=c(1,2))
acf(abs, ci.type="ma",main=" ACF for abs. returns")
pacf(abs, main=" PACF plot for abs.returns")
```


##From ACF and PACF we see many lags are significant. Hence, we plot EACF to get the candidate models

```{r}
eacf(abs) 
```

##From the squared returns ACF and PACF plot, it is not that clear to derive the order of p and q. Hence, I approach EACF and the order of ARMA are ARMA (2,3), ARMA (3,3), ARMA (2,4). Thus, GARCH candidate models would be GARCH (3,2) GARCH (3,3) GARCH (4,2)

```{r}


par(mfrow=c(1,2))
acf(sqr, ci.type="ma",main="ACF  for sqr. return")
pacf(sqr, main="PACF for sqr. return")
```

##

```{r}
eacf(sqr) 
```



### With reference to the Dickey-Fuller Test, p-value is less than the 0.02 and we can reject the null hypothesis stating the non-stationarity. Hence , we can proceed further for model selection .


#MODEL ESTIMATION:
##GARCH (2,1): for GBP and CAD Curruency Pair


```{r}


# GARCH(2,1)
library(tseries)
GBPCADGARCHFit.21 = garch(DifflogGBPCADGarch,order=c(2,1),trace =FALSE)
summary(GBPCADGARCHFit.21)
```



## GARCH (2,2):
##This model can be interpreted as an overfit model of GARCH(2,1) and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

```{r}

GBPCADGARCHFit.22 = garch(DifflogGBPCADGarch, order =c(2,2),trace =FALSE)
summary(GBPCADGARCHFit.22)
```


##GARCH (3,1):
##This model can be interpreted as an overfit model of GARCH(2,1) and GARCH (2,2). This model may not be consider to be a good fit.



```{r}

GBPCADGARCHFit.31 = garch(DifflogGBPCADGarch,order=c(3,1),trace =FALSE)
summary(GBPCADGARCHFit.31)
```


##GARCH (3,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

# GARCH(3,2) 

```{r}
GBPCADGARCHFit.32 = garch(DifflogGBPCADGarch,order=c(3,2),trace =FALSE)
summary(GBPCADGARCHFit.32)
```


## GARCH (3,3):
This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not consider to be a good fit.

# GARCH(3,3)

```{r}

GBPCADGARCHFit.33 = garch(DifflogGBPCADGarch,order=c(3,3),trace =FALSE)
summary(GBPCADGARCHFit.33)
```


##GARCH (4,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not considered to be a good fit.



```{r}

GBPCADGARCHFit.11 = garch(DifflogGBPCADGarch,order=c(1,1),trace =FALSE)
summary(GBPCADGARCHFit.11)
```



# Model Selection:
##Best possible model is selected by AIC scores of the models. From the below sort function, GARCH(3,1) would be the best model for the return series. From the p-value, 3.1 also has the lowest correlation


```{r}
library(dLagM)
GARCHModelSelectionGBPCAD = AIC(GBPCADGARCHFit.21,GBPCADGARCHFit.22 ,GBPCADGARCHFit.31,GBPCADGARCHFit.32,GBPCADGARCHFit.33, GBPCADGARCHFit.11)
sortScore(GARCHModelSelectionGBPCAD, score ="aic")
```


# Model Fitting:

```{r}
library(rugarch)
GBPCADmodel1.1<-ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1,1)), 
                  mean.model = list(armaOrder = c(2,2), include.mean = TRUE), 
                  distribution.model = "norm")
                  
GBPCADgarchMODEL1.1<-ugarchfit(spec=GBPCADmodel1.1,data=DifflogGBPCADGarch, out.sample = 100)
plot(GBPCADgarchMODEL1.1,which="all")
```

##Model Diagnostics

```{r}
GBPCADgarchMODEL1.1
```






## Forecasting

```{r}
forcgarchGBPCAD= ugarchforecast(GBPCADgarchMODEL1.1, data = DiffGBPCADLogTran, n.ahead = 100, n.roll =10)
print(forcgarchGBPCAD)
```




## Forecasting the rate


```{r}
p.t_1 = 1.73964
  R_t <- c(  0.0118094, 0.0277190, -0.0126465, -0.0376338, -0.0040782, 0.0281764, 0.0029715, -0.0344221, -0.0185737, 0.0216456, 0.0155935, -0.0250896, -0.0287104, 0.0101600, 0.0227997, -0.0121885, -0.0327238, -0.0033753, 0.0235475, 
0.0012010, -0.0303177, -0.0158838, 0.0182685, 0.0121764, -0.0225930, -0.0247895, 0.0086410, 0.0186159, -0.0116855,  -0.0285215, -0.0028821, 0.0195603, -0.0002144, -0.0267566, -0.0136678, 0.0153109, 0.0093202, -0.0203746, -0.0214814, 0.0072500, 0.0150604, -0.0111603, -0.0249272, -0.0025529, 0.0161284, -0.0013397, -0.0236696, -0.0118461,0.0127238, 0.0069357, -0.0184073, -0.0186927, 0.0059826, 0.0120410, -0.0106302, -0.0218553, -0.0023509, 0.0131766, -0.0022283,
-0.0209959, -0.0103523, 0.0104634, 0.0049479, -0.0166662, -0.0163441,  0.0048328, 0.0094788, -0.0101078, -0.0192314, 
-0.0022463, 0.0106395, -0.0029247, -0.0186821, -0.0091304, 0.0084906, 0.0032929, -0.0151278, -0.0143681, 0.0037938 , 
0.0073062, -0.0096024, -0.0169920, -0.0022152, 0.0084604, -0.0034654, -0.0166813, -0.0081339, 0.0067708, 0.0019171,
-0.0137710, -0.0127071, 0.0028582, 0.0054655, -0.0091201, -0.0150819, -0.0022387,  0.0065901, -0.0038806, -0.0149527, 
-0.0073236 
)
  p_t= 0
  for (i in 1:100){
    p_t =  p.t_1  *((2.71828)^(R_t[i]/100))
   print(p_t)
    p.t_1=p_t
  }
  
```



```{r}
RateGBPJPYGarch = 141.168
  RGBPJPYGARCH <-c(

)
  GBPJPYgarch= 0
  for (i in 1:100){
    USCanadagarch =  RateGBPJPYGarch *((2.71828)^(RGBPJPYGARCH[i]/100))
    print(GBPJPYgarch)
    RateUSGBPJPY=GBPJPYgarch
  }
  
```







