---
title: "GARCH Model EUR And JPY"
author: "Jane"
date: "29/04/2021"
output:
  pdf_document: default
  html_document: default
---




# Forcasting Exchange Rate Using GARCH Model for EUR And JPY
## Reading EUR and JPY Currency into r


```{r}
library(readr)
library(dplyr)
EURJPYGARCH<-  read.csv ("EURJPY_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateEURJPY = ("CLOSE"))

  
head(EURJPYGARCH)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

EURJPYGARCH$Date <- lubridate::ymd(EURJPYGARCH$Date)
head(EURJPYGARCH)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(EURJPYGARCH))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
EURJPYGARCHTS<- ts(as.vector(EURJPYGARCH$Rate),  frequency = 322, start= c(2000,01,03))
plot.ts(EURJPYGARCHTS)
title("Time Series plot of EURJPYTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```








##Dealing with Conditional Heteroscedaticity:


```{r}
 
DifflogEURJPYGarch= diff(log(EURJPYGARCHTS))*100
plot(DifflogEURJPYGarch)
title("Plot of returns of EURJPY", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```

##nature as almost at all lags the p-values fall below the significance levels.



```{r}
library(TSA)
McLeod.Li.test(y= DifflogEURJPYGarch,main="McLeod-Li test statistics for Daily return series")
```



## In order to get an order of GARCH , we further transform the return series into absolute values and squared return values.


```{r}

abs = abs(DifflogEURJPYGarch)
sqr = DifflogEURJPYGarch^2
```




# GARCH Model specification:

```{r}
par(mfrow=c(1,2))
acf(abs, ci.type="ma",main=" ACF for abs. returns")
pacf(abs, main=" PACF plot for abs.returns")
```


##From ACF and PACF we see many lags are significant. Hence, we plot EACF to get the candidate models

```{r}
eacf(abs) 
```

##From the squared returns ACF and PACF plot, it is not that clear to derive the order of p and q. Hence, I approach EACF and the order of ARMA are ARMA (2,3), ARMA (3,3), ARMA (2,4). Thus, GARCH candidate models would be GARCH (3,2) GARCH (3,3) GARCH (4,2)

```{r}


par(mfrow=c(1,2))
acf(sqr, ci.type="ma",main="ACF  for sqr. return")
pacf(sqr, main="PACF for sqr. return")
```

##

```{r}
eacf(sqr) 
```



### With reference to the Dickey-Fuller Test, p-value is less than the 0.02 and we can reject the null hypothesis stating the non-stationarity. Hence , we can proceed further for model selection .


#MODEL ESTIMATION:
##GARCH (2,1): for GBP and USD Curruency Pair


```{r}


# GARCH(2,1)
library(tseries)
EURJPYGARCHFit.21 = garch(DifflogEURJPYGarch,order=c(2,1),trace =FALSE)
summary(EURJPYGARCHFit.21)
```



## GARCH (2,2):
##This model can be interpreted as an overfit model of GARCH(2,1) and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

```{r}

EURJPYGARCHFit.22 = garch(DifflogEURJPYGarch, order =c(2,2),trace =FALSE)
summary(EURJPYGARCHFit.22)
```


##GARCH (3,1):
##This model can be interpreted as an overfit model of GARCH(2,1) and GARCH (2,2). This model may not be consider to be a good fit.



```{r}

EURJPYGARCHFit.31 = garch(DifflogEURJPYGarch,order=c(3,1),trace =FALSE)
summary(EURJPYGARCHFit.31)
```


##GARCH (3,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

# GARCH(3,2) 

```{r}
EURJPYGARCHFit.32 = garch(DifflogEURJPYGarch,order=c(3,2),trace =FALSE)
summary(EURJPYGARCHFit.32)
```


## GARCH (3,3):
This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not consider to be a good fit.

# GARCH(3,3)

```{r}

EURJPYGARCHFit.33 = garch(DifflogEURJPYGarch,order=c(3,3),trace =FALSE)
summary(EURJPYGARCHFit.33)
```


##GARCH (4,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not considered to be a good fit.



```{r}

EURJPYGARCHFit.42 = garch(DifflogEURJPYGarch,order=c(4,2),trace =FALSE)
summary(EURJPYGARCHFit.42)
```
  ##
  
```{r}

EURJPYGARCHFit.41 = garch(DifflogEURJPYGarch,order=c(4,1),trace =FALSE)
summary(EURJPYGARCHFit.41)
```


# Model Selection:
##Best possible model is selected by AIC scores of the models. From the below sort function, GARCH(3,1) would be the best model for the return series. From the p-value, 3.1 also has the lowest correlation


```{r}
library(dLagM)
GARCHModelSelectionEURJPY = AIC(EURJPYGARCHFit.21,EURJPYGARCHFit.22 ,EURJPYGARCHFit.31,EURJPYGARCHFit.32,EURJPYGARCHFit.33, EURJPYGARCHFit.42, EURJPYGARCHFit.41)
sortScore(GARCHModelSelectionEURJPY, score ="aic")
```


# Model Fitting:

```{r}
library(rugarch)
EURJPYmodel1.1<-ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1,1)), 
                  mean.model = list(armaOrder = c(1,6), include.mean = TRUE), 
                  distribution.model = "norm")
                  
EURJPYgarchMODEL1.1<-ugarchfit(spec=EURJPYmodel1.1,data=DifflogEURJPYGarch, out.sample = 100)
plot(EURJPYgarchMODEL1.1,which="all")
```

##Model Diagnostics

```{r}
EURJPYgarchMODEL1.1
```


## Forecasting

```{r}
forcgarchEURJPY= ugarchforecast(EURJPYgarchMODEL1.1, data = DiffEURJPYLogTran, n.ahead = 100, n.roll =10)
print(forcgarchEURJPY)
```


## plotting

```{r}
plot(forcgarchEURJPY, which= "all")
```

## Forecasting the rate


```{r}
p.t_1 = 126.121
  R_t <- c(  0.011383, -0.001507, 0.003220, 0.006640, 0.006263, 0.006325, 0.006559, 0.006778, 0.006982, 0.007172, 0.007349, 0.007515, 0.007669, 0.007813, 0.007947, 0.008072, 0.008188, 0.008297, 0.008399, 0.008493, 0.008581, 
0.008664, 0.008740, 0.008812, 0.008879, 0.008941, 0.008999, 0.009053, 0.009104, 0.009151, 0.009194, 0.009235, 0.009274 , 0.009309, 0.009342, 0.009373, 0.009402, 0.009429, 0.009454, 0.009478, 0.009499, 0.009520, 0.009539, 0.009556, 0.009573, 0.009588, 0.009603, 0.009616, 0.009629, 0.009640, 0.009651, 0.009661, 0.009671, 0.009679, 0.009688, 0.009695 , 0.009702, 0.009709, 0.009715, 0.009721, 0.009727, 0.009732, 0.009736, 0.009741, 0.009745, 0.009749, 0.009752, 
0.009755, 0.009759, 0.009761, 0.009764, 0.009767, 0.009769, 0.009771, 0.009773, 0.009775, 0.009777, 0.009778, 0.009780 , 0.009781, 0.009783, 0.009784, 0.009785, 0.009786, 0.009787, 0.009788, 0.009789, 0.009790, 0.009791, 0.009791, 0.009792, 0.009793, 0.009793, 0.009794, 0.009794, 0.009795, 0.009795, 0.009796, 0.009796, 0.009796


)
  p_t= 0
  for (i in 1:100){
    p_t =  p.t_1  *((2.71828)^(R_t[i]/100))
   print(p_t)
    p.t_1=p_t
  }
  
```









