P---
title: "GARCH Model"
author: "Jane"
date: "19/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Forcasting Exchange Rate Using GARCH Model



## Reading Canadian and Japanes Currency into r
```{r}
library(readr)
library(dplyr)
CanJapCurrency <- readxl::read_xlsx ("CADJPY_Candlestick_1_D_BID_01.01.2000-31.12.2020.xlsx")%>%
  select('Gmt time', Close)%>%
  rename(Date = ('Gmt time'), Rate = ("Close"))

head(CanJapCurrency)
```


## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

CanJapCurrency$Date <- lubridate::ymd(CanJapCurrency$Date)
head(CanJapCurrency)

```



##Checking for obvious errors
```{r}
#Checking for obvious errors
which(is.na(CanJapCurrency))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
CanjapTS<- ts(as.vector(CanJapCurrency$Rate),  frequency = 314, start= c(2000,01,03))
plot.ts(CanjapTS)
title("Time Series plot of CanJapTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```


## Automatic Colleration and Partial Automatic Correlation
##The ACF plot clearly states the high correlation among successive points. It also shows a strong evidence of an existence of a trend as expected from the time series plot. The PACF plot shows one significant correlation on the plot. Unit root test proves the nature of non-stationarity of the series.


```{r}

par(mfrow=c(1,2))
acf(CanjapTS, main=" ACF ")
pacf(CanjapTS, main=" PACF ")
```



```{r}
ar(diff(CanjapTS))
```



##Augmented Dickey-Fuller test
##The Augmented Dickey-Fuller test allows for higher-order autoregressive processes 

```{r}
library(tseries)
adf.test(CanjapTS, alternative = "stationary", k = 0)
```

##Ensuring the stationarity of the series:
##Transformation:Natural Logarithmic transformation is one of the best approach to look for stationarity of the sereis.


```{r}


CanJapLogTran<-log(CanjapTS)

ar(CanJapLogTran)
```


## Augmented Dickey-Fuller Test for log Tranformation

```{r}
adf.test(CanJapLogTran, alternative = "stationary", k = 0)
```


## ACF and PACF for log transformation
## The ACF and PACF plot are similar to the original series and we can still suspect the non-stationarity of the series and this is also supported by Unit root test.
```{r}


par(mfrow=c(1,2))
acf(CanJapLogTran, ci.type='ma', main=" ACF of transformed data")

pacf(CanJapLogTran,  main="PACF of transformed data")

```


##Differencing as my next approach to achieve the stationarity of the series.


```{r}
DiffCanJapLogTran<-diff(CanJapLogTran) 
ar(DiffCanJapLogTran)
```


## Runing ACF and PACF for the log transform Difference

##At the first difference of the transformed series, we can observe the plots of ACF and PACF shows a bit difference to the previous steep decreasing pattern. As we can ensure the assumption of stationarity with Unit-Root test.

```{r}


par(mfrow=c(1,2))
acf(DiffCanJapLogTran, ci.type='ma', main="ACF of 1st differnce")
pacf(DiffCanJapLogTran, main="PACF of 1st differnce")
```


## Augmented Dickey-Fuller Test for log Tranformation Difference

```{r}
adf.test(DiffCanJapLogTran, alternative = "stationary", k = 0)
```
### With reference to the Dickey-Fuller Test, p-value is less than the 0.02 and we can reject the null hypothesis stating the non-stationarity. Hence , we can proceed further for model selection .


#MODEL ESTIMATION:
##GARCH (2,1): for Canadian and Japanese Curruency Pair


```{r}


# GARCH(2,1)
CanJapGARCHFit.21 = garch(DiffCanJapLogTran,order=c(2,1),trace =FALSE)
summary(CanJapGARCHFit.21)
```



## GARCH (2,2):
##This model can be interpreted as an overfit model of GARCH(2,1) and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

```{r}


CanJapGARCHFit.22 = garch(DiffCanJapLogTran, order =c(2,2),trace =FALSE)
summary(CanJapGARCHFit.22)
```


##GARCH (3,1):
##This model can be interpreted as an overfit model of GARCH(2,1) and GARCH (2,2). This model may not be consider to be a good fit.



```{r}

CanJapGARCHFit.31 = garch(DiffCanJapLogTran,order=c(3,1),trace =FALSE)
summary(CanJapGARCHFit.31)
```


##GARCH (3,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

# GARCH(3,2) 

```{r}
CanJapGARCHFit.32 = garch(DiffCanJapLogTran,order=c(3,2),trace =FALSE)
summary(CanJapGARCHFit.32)
```


## GARCH (3,3):
This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not consider to be a good fit.

# GARCH(3,3)

```{r}

CanJapGARCHFit.33 = garch(DiffCanJapLogTran,order=c(3,3),trace =FALSE)
summary(CanJapGARCHFit.33)
```


##GARCH (4,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not considered to be a good fit.



```{r}

CanJapGARCHFit.42 = garch(DiffCanJapLogTran,order=c(4,2),trace =FALSE)
summary(CanJapGARCHFit.42)
```


#Model Selection:

##Best possible model is selected by AIC scores of the models. From the below sort function, GARCH(2,1) would be the best model for the return series.

```{r}
library(dLagM)
GARCHModelSelectionCanJap = AIC(CanJapGARCHFit.21,CanJapGARCHFit.22 ,CanJapGARCHFit.31,CanJapGARCHFit.32,CanJapGARCHFit.33, CanJapGARCHFit.42)
sortScore(GARCHModelSelectionCanJap, score ="aic")
```


# Model Fitting:

```{r}
library(rugarch)
CanJapmodel2.1<-ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(2, 2)), 
                  mean.model = list(armaOrder = c(1, 1), include.mean = TRUE), 
                  distribution.model = "norm")
                  
MODEL2.1<-ugarchfit(spec=CanJapmodel2.1,data=DiffCanJapLogTran, out.sample = 100)
plot(MODEL2.1,which="all")
```

##Model Diagnostics

```{r}
MODEL2.1
```


## Forecasting

```{r}
forc = ugarchforecast(MODEL2.1, data = DiffCanJapLogTran, n.ahead = 100, n.roll =10)
print(forc)
```


## plotting

```{r}
plot(forc, which= "all")
```
##
```{r}
p.t_1 = 81.074
  R_t <-c(0.005572, 0.005672, 0.005652, 0.005696, 0.005705, 0.005733, 0.005750, 0.005772, 0.005792, 0.005812, 0.005832, 0.005851, 0.005871, 0.005890, 0.005909, 0.005927, 0.005946, 0.005964, 0.005982, 0.006000, 0.006018, 0.006036, 0.006053, 0.006070, 0.006087, 0.006104, 0.006120, 0.006137, 0.006153, 0.006169, 0.006185, 0.006201, 0.006216, 0.006232, 0.006247, 0.006262, 0.006277, 0.006292, 0.006307, 0.006321, 0.006335, 0.006350, 0.006364, 0.006378, 0.006391, 0.006405, 0.006418, 0.006432, 0.006445, 0.006458, 0.006471, 0.006484, 0.006497, 0.006509, 0.006522, 0.006534, 0.006546, 0.006558, 0.006570, 0.006582, 0.006594, 0.006606, 0.006617, 0.006629, 0.006640, 0.006651, 0.006662, 0.006673, 0.006684, 0.006695, 0.006705, 0.006716, 0.006726, 0.006737, 0.006747, 0.006757, 0.006767, 0.006777, 0.006787, 0.006797, 0.006807, 0.006816, 0.006826, 0.006835, 0.006845, 0.006854, 0.006863, 0.006872, 0.006881, 0.006890, 0.006899, 0.006908, 0.006916, 0.006925, 0.006934, 0.006942, 0.006950, 0.006959, 0.006967, 0.006975)
  p_t= 0 
  for (i in 1:100){
    p_t =  p.t_1 *((2.71828)^(R_t[i]/100))
    print(p_t)
    p.t_1=p_t
  }
  
```





































