---
title: "GARCH Model EUR And GBP"
author: "Jane"
date: "29/04/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---




# Forcasting Exchange Rate Using GARCH Model for EUR And GBP
## Reading EUR and GBP Currency into r


```{r}
library(readr)
library(dplyr)
EURGBPGARCH<-  read.csv ("EURGBP_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateEURGBP = ("CLOSE"))

  
head(EURGBPGARCH)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

EURGBPGARCH$Date <- lubridate::ymd(EURGBPGARCH$Date)
head(EURGBPGARCH)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(EURGBPGARCH))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
EURGBPGARCHTS<- ts(as.vector(EURGBPGARCH$Rate),  frequency = 322, start= c(2000,01,03))
plot.ts(EURGBPGARCHTS)
title("Time Series plot of EURGBPTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```








##Dealing with Conditional Heteroscedaticity:


```{r}
 
DifflogEURGBPGarch= diff(log(EURGBPGARCHTS))*100
plot(DifflogEURGBPGarch)
title("Plot of returns of EURGBP", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```

##nature as almost at all lags the p-values fall below the significance levels.



```{r}
library(TSA)
McLeod.Li.test(y= DifflogEURGBPGarch,main="McLeod-Li test statistics for Daily return series")
```



## In order to get an order of GARCH , we further transform the return series into absolute values and squared return values.


```{r}

abs = abs(DifflogEURGBPGarch)
sqr = DifflogEURGBPGarch^2
```




# GARCH Model specification:

```{r}
par(mfrow=c(1,2))
acf(abs, ci.type="ma",main=" ACF for abs. returns")
pacf(abs, main=" PACF plot for abs.returns")
```


##From ACF and PACF we see many lags are significant. Hence, we plot EACF to get the candidate models

```{r}
eacf(abs) 
```

##From the squared returns ACF and PACF plot
```{r}


par(mfrow=c(1,2))
acf(sqr, ci.type="ma",main="ACF  for sqr. return")
pacf(sqr, main="PACF for sqr. return")
```

##

```{r}
eacf(sqr) 
```



### With reference to the Dickey-Fuller Test, p-value is less than the 0.02 and we can reject the null hypothesis stating the non-stationarity. Hence , we can proceed further for model selection .


#MODEL ESTIMATION:
##GARCH (1,1): for GBP and USD Curruency Pair


```{r}


# GARCH(2,1)
library(tseries)
EURGBPGARCHFit.11= garch(DifflogEURGBPGarch,order=c(1,1),trace =FALSE)
summary(EURGBPGARCHFit.11)
```



## GARCH (2,2):
##This model can be interpreted as an overfit model of GARCH(1,1) and p values from residual tests confirms that residuals has low correlated. Thus this model is not consider to be a good fit.

```{r}

EURGBPGARCHFit.22 = garch(DifflogEURGBPGarch, order =c(2,2),trace =FALSE)
summary(EURGBPGARCHFit.22)
```


##GARCH (3,1):
##This model can be interpreted as an overfit model of GARCH(2,1) and GARCH (2,2). This model may not be consider to be a good fit.



```{r}

EURGBPGARCHFit.31 = garch(DifflogEURGBPGarch,order=c(3,1),trace =FALSE)
summary(EURGBPGARCHFit.31)
```


##GARCH (3,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

# GARCH(3,2) 

```{r}
EURGBPGARCHFit.32 = garch(DifflogEURGBPGarch,order=c(3,2),trace =FALSE)
summary(EURGBPGARCHFit.32)
```


## GARCH (3,3):
## This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not consider to be a good fit.

# GARCH(3,3)

```{r}

EURGBPGARCHFit.33 = garch(DifflogEURGBPGarch,order=c(3,3),trace =FALSE)
summary(EURGBPGARCHFit.33)
```


##GARCH (4,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not considered to be a good fit.



```{r}

EURGBPGARCHFit.42 = garch(DifflogEURGBPGarch,order=c(4,2),trace =FALSE)
summary(EURGBPGARCHFit.42)
```
  ##
  
```{r}

EURGBPGARCHFit.41 = garch(DifflogEURGBPGarch,order=c(4,1),trace =FALSE)
summary(EURGBPGARCHFit.41)
```


# Model Selection:
##Best possible model is selected by AIC scores of the models. From the below sort function, GARCH(3,1) would be the best model for the return series. From the p-value, 3.1 also has the lowest correlation


```{r}
library(dLagM)
GARCHModelSelectionEURGBP = AIC(EURGBPGARCHFit.11,EURGBPGARCHFit.22 ,EURGBPGARCHFit.31,EURGBPGARCHFit.32,EURGBPGARCHFit.33, EURGBPGARCHFit.42, EURGBPGARCHFit.41)
sortScore(GARCHModelSelectionEURGBP, score ="aic")
```


# Model Fitting:

```{r}
library(rugarch)
EURGBPmodel1.1<-ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1,1)), 
                  mean.model = list(armaOrder = c(6,4), include.mean = TRUE), 
                  distribution.model = "norm")
                  
EURGBPgarchMODEL1.1<-ugarchfit(spec=EURGBPmodel1.1,data=DifflogEURGBPGarch, out.sample = 100)
plot(EURGBPgarchMODEL1.1,which="all")
```

##Model Diagnostics

```{r}
EURGBPgarchMODEL1.1
```


## Forecasting

```{r}
forcgarchEURGBP= ugarchforecast(EURGBPgarchMODEL1.1, data = DifflogEURGBPGarch, n.ahead = 100, n.roll = 10)
print(forcgarchEURGBP)
```


## plotting

```{r}
plot(forcgarchEURGBP, which= "all")
```

## Forecasting the rate


```{r}
p.t_1 = 0.89365
  R_t <- c(-0.0175020, 0.0238688, -0.0096144, 0.0164705, -0.0011654, 0.0137289, -0.0007232, 0.0116537, -0.0002277, 0.0098904, 0.0004323, 0.0081169, 0.0012552, 0.0063438, 0.0022094, 0.0045913, 0.0032507, 0.0028840, 0.0043354, 0.0012485, 0.0054215, -0.0002880, 0.0064697, -0.0016996, 0.0074436, -0.0029618, 0.0083107, -0.0040527, 0.0090426, -0.0049536, 0.0096160, -0.0056500, 0.0100124, -0.0061315, 0.0102191, -0.0063924, 0.0102285, -0.0064322, 0.0100390 , -0.0062551, 0.0096543,  -0.0058704,  0.0090835 , -0.0052920,  0.0083405,  -0.0045383, 0.0074438, -0.0036315, 0.0064158 , -0.0025972, 0.0052821, -0.0014637, 0.0040710, -0.0002614, 0.0028126, 0.0009780, 0.0015380, 0.0022224, 0.0002787 ,  0.0034401, -0.0009348, 0.0046002, -0.0020729, 0.0056739, -0.0031084 , 0.0066347, -0.0040166, 0.0074593, -0.0047765 , 0.0081281, -0.0053708, 0.0086257, -0.0057864,  0.0089411, -0.0060148, 0.0090679, -0.0060524, 0.0090048, -0.0059001 ,
0.0087549, -0.0055638, 0.0083263, -0.0050538, 0.0077313, -0.0043847, 0.0069864, -0.0035747, 0.0061115, -0.0026455, 
0.0051298, -0.0016218,  0.0040668, -0.0005299, 0.0029499, 0.0006020, 0.0018074, 0.0017452, 0.0006683, 0.0028710 , 
-0.0004391






)
  p_t= 0
  for (i in 1:100){
    p_t =  p.t_1  *((2.71828)^(R_t[i]/100))
   print(p_t)
    p.t_1=p_t
  }
  
```









