---
title: "GARCH Model GBP And USD"
author: "Jane"
date: "28/04/2021"
output:
  pdf_document: default
  html_document: default
---




# Forcasting Exchange Rate Using GARCH Model for GBP And USDollar

## Reading GBP and USD Currency into r
```{r}
library(readr)
library(dplyr)
GBPUSDGARCH <-  read.csv ("GBPUSD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateUSDGBP = ("CLOSE"))

  
tail(GBPUSDGARCH)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

GBPUSDGARCH$Date <- lubridate::ymd(GBPUSDGARCH$Date)
head(GBPUSDGARCH)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(GBPUSDGARCH))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
GBPUSDGARCHTS<- ts(as.vector(GBPUSDGARCH$Rate),  frequency = 320, start= c(2000,01,03))
plot.ts(GBPUSDGARCHTS)
title("Time Series plot of GBPUSDTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```








##Dealing with Conditional Heteroscedaticity:


```{r}
 
DifflogGBPUSDGarch= diff(log(GBPUSDGARCHTS))*100
plot(DifflogGBPUSDGarch)
title("Plot of returns of GBPUSD", sub = "(2013-2018)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```

##nature as almost at all lags the p-values fall below the significance levels.



```{r}
library(TSA)
McLeod.Li.test(y= DifflogGBPUSDGarch,main="McLeod-Li test statistics for Daily return series")
```



## In order to get an order of GARCH , we further transform the return series into absolute values and squared return values.


```{r}

abs = abs(DifflogGBPUSDGarch)
sqr = DifflogGBPUSDGarch^2
```




# GARCH Model specification:

```{r}
par(mfrow=c(1,2))
acf(abs, ci.type="ma",main=" ACF for abs. returns")
pacf(abs, main=" PACF plot for abs.returns")
```


##From ACF and PACF we see many lags are significant. Hence, we plot EACF to get the candidate models

```{r}
eacf(abs) 
```

##From the squared returns ACF and PACF plot, it is not that clear to derive the order of p and q. Hence, I approach EACF and the order of ARMA are ARMA (2,3), ARMA (3,3), ARMA (2,4). Thus, GARCH candidate models would be GARCH (3,2) GARCH (3,3) GARCH (4,2)

```{r}


par(mfrow=c(1,2))
acf(sqr, ci.type="ma",main="ACF  for sqr. return")
pacf(sqr, main="PACF for sqr. return")
```

##

```{r}
eacf(sqr) 
```



### With reference to the Dickey-Fuller Test, p-value is less than the 0.02 and we can reject the null hypothesis stating the non-stationarity. Hence , we can proceed further for model selection .


#MODEL ESTIMATION:
##GARCH (2,1): for GBP and CAD Curruency Pair


```{r}


# GARCH(2,1)
library(tseries)
GBPUSDGARCHFit.21 = garch(DifflogGBPUSDGarch,order=c(2,1),trace =FALSE)
summary(GBPUSDGARCHFit.21)
```



## GARCH (2,2):
##This model can be interpreted as an overfit model of GARCH(2,1) and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

```{r}

GBPUSDGARCHFit.22 = garch(DifflogGBPUSDGarch, order =c(2,2),trace =FALSE)
summary(GBPUSDGARCHFit.22)
```


##GARCH (3,1):
##This model can be interpreted as an overfit model of GARCH(2,1) and GARCH (2,2). This model may not be consider to be a good fit.



```{r}

GBPUSDGARCHFit.31 = garch(DifflogGBPUSDGarch,order=c(3,1),trace =FALSE)
summary(GBPUSDGARCHFit.31)
```


##GARCH (3,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

# GARCH(3,2) 

```{r}
GBPUSDGARCHFit.32 = garch(DifflogGBPUSDGarch,order=c(3,2),trace =FALSE)
summary(GBPUSDGARCHFit.32)
```


## GARCH (3,3):
This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not consider to be a good fit.

# GARCH(3,3)

```{r}

GBPUSDGARCHFit.33 = garch(DifflogGBPUSDGarch,order=c(3,3),trace =FALSE)
summary(GBPUSDGARCHFit.33)
```


##GARCH (4,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not considered to be a good fit.



```{r}

GBPUSDGARCHFit.11 = garch(DifflogGBPUSDGarch,order=c(1,1),trace =FALSE)
summary(GBPUSDGARCHFit.11)
```



# Model Selection:
##Best possible model is selected by AIC scores of the models. From the below sort function, GARCH(3,1) would be the best model for the return series. From the p-value, 3.1 also has the lowest correlation


```{r}
library(dLagM)
GARCHModelSelectionGBPUSD = AIC(GBPUSDGARCHFit.21,GBPUSDGARCHFit.22 ,GBPUSDGARCHFit.31,GBPUSDGARCHFit.32,GBPUSDGARCHFit.33, GBPUSDGARCHFit.11)
sortScore(GARCHModelSelectionGBPUSD, score ="aic")
```


# Model Fitting:

```{r}
library(rugarch)
GBPUSDmodel1.1<-ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1,1)), 
                  mean.model = list(armaOrder = c(2, 2), include.mean = TRUE), 
                  distribution.model = "norm")
                  
GBPUSDgarchMODEL1.1<-ugarchfit(spec=GBPUSDmodel1.1,data=DifflogGBPUSDGarch, out.sample = 100)
plot(GBPUSDgarchMODEL1.1,which="all")
```

##Model Diagnostics

```{r}
GBPUSDgarchMODEL1.1
```


## Forecasting

```{r}
forcgarchGBPUSD= ugarchforecast(GBPUSDgarchMODEL1.1, data = DiffGBPUSDLogTran, n.ahead = 100, n.roll =10)
print(forcgarchGBPUSD)
```


## plotting

```{r}
plot(forcgarchGBPUSD, which= "all")
```

## Forecasting the rate


```{r}
p.t_1 =1.36630	
  R_t <- c( -0.0186898, -0.0057243, 0.0343171, -0.0269843, 0.0074931,  0.0265472, -0.0306860, 0.0196746, 0.0154778, 
-0.0293684, 0.0290539, 0.0028231, -0.0233549, 0.0343227, -0.0095134, -0.0136515, 0.0348117, -0.0197243, -0.0017814, 0.0305719, -0.0263615, 0.0104523, 0.0223493, -0.0285403, 0.0212399, 0.0114567, -0.0260549, 0.0290308, -0.0004338,
-0.0193913, 0.0327557, -0.0115466, -0.0096379, 0.0319710, -0.0202660, 0.0016900, 0.0269086, -0.0253705, 0.0128848, 0.0184237, -0.0262019, 0.0223021, 0.0078534, -0.0227480, 0.0286017, -0.0031929, -0.0156275, 0.0309369, -0.0130771, -0.0059831, 0.0290661, -0.0203743, 0.0047009, 0.0233730, -0.0240773, 
0.0148250, 0.0147941, -0.0237337, 0.0229138, 0.0046664, -0.0194983, 0.0278292, -0.0054796, -0.0120948, 0.0289294, -0.0141502, -0.0026946, 0.0261509, -0.0201071, 0.0072675, 0.0200026, -0.0225437, 0.0163106, 0.0114763, -0.0211920, 0.0231275, 0.0018881, -0.0163486, 0.0267724, -0.0073233, -0.0088164, 0.0267904, -0.0148121, 
0.0002268, 0.0232724, -0.0195203, 0.0094110, 0.0168273, -0.0208266, 0.0173808, 0.0084792, -0.0186266, 
0.0229947, -0.0004943, -0.0133343, 0.0254869, -0.0087562, -0.0058084, 0.0245713
-0.0151090, -0.0151090









)
  p_t= 0
  for (i in 1:100){
    p_t =  p.t_1  *((2.71828)^(R_t[i]/100))
   print(p_t)
    p.t_1=p_t
  }
  
```



```{r}
RateGBPJPYGarch = 141.168
  RGBPJPYGARCH <-c(
)
  GBPJPYgarch= 0
  for (i in 1:100){
    USCanadagarch =  RateGBPJPYGarch *((2.71828)^(RGBPJPYGARCH[i]/100))
    print(GBPJPYgarch)
    RateUSGBPJPY=GBPJPYgarch
  }
  
```







