---
title: "GARCH Model USCanada"
author: "Jane"
date: "27/04/2021"
output:
  pdf_document: default
  html_document: default
---




# Forcasting Exchange Rate Using GARCH Model for US Dollar and Canadaian Dolla

## Reading Canadian and Canaada Currency into r
```{r}
library(readr)
library(dplyr)
USDCADCurrencyGARCH <-  read.csv ("USDCAD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateUSCAD = ("CLOSE"))

  
head(USDCADCurrencyGARCH)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

USDCADCurrencyGARCH$Date <- lubridate::ymd(USDCADCurrencyGARCH$Date)
head(USDCADCurrencyGARCH)

```



##Checking for obvious errors
```{r}
#Checking for obvious errors
which(is.na(USDCADCurrencyGARCH))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
USDCADGARCHTS<- ts(as.vector(USDCADCurrencyGARCH$Rate),  frequency = 314, start= c(2000,01,03))
plot.ts(USDCADGARCHTS)
title("Time Series plot of USDCADTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```


## Automatic Colleration and Partial Automatic Correlation
##The ACF plot clearly states the high correlation among successive points. It also shows a strong evidence of an existence of a trend as expected from the time series plot. The PACF plot shows one significant correlation on the plot. Unit root test proves the nature of non-stationarity of the series.


```{r}

par(mfrow=c(1,2))
acf(USDCADGARCHTS, main=" ACF ")
pacf(USDCADGARCHTS, main=" PACF ")
```




## Differening the series to ensure stationality

```{r}
ar(diff(USDCADGARCHTS))
```



##Augmented Dickey-Fuller test
##The Augmented Dickey-Fuller test allows for higher-order autoregressive processes 

```{r}
library(tseries)
adf.test(USDCADGARCHTS, alternative = "stationary", k = 0)
```

##Ensuring the stationarity of the series:
##Transformation:Natural Logarithmic transformation is one of the best approach to look for stationarity of the sereis.


```{r}


USDCADLogTranGARCH<-log(USDCADGARCHTS)

ar(USDCADLogTranGARCH)
```


## Augmented Dickey-Fuller Test for log Tranformation

```{r}
adf.test(USDCADLogTranGARCH, alternative = "stationary", k = 0)
```


## ACF and PACF for log transformation
## The ACF and PACF plot are similar to the original series and we can still suspect the non-stationarity of the series and this is also supported by Unit root test.
```{r}


par(mfrow=c(1,2))
acf(USDCADLogTranGARCH, ci.type='ma', main=" ACF of transformed data")

pacf(USDCADLogTranGARCH,  main="PACF of transformed data")

```


##Differencing as my next approach to achieve the stationarity of the series.


```{r}
DiffUSDCADLogTranGARCH<-diff(USJapLogTranGARCH) 
ar(DiffUSDCADLogTranGARCH)
```


## Runing ACF and PACF for the log transform Difference

##At the first difference of the transformed series, we can observe the plots of ACF and PACF shows a bit difference to the previous steep decreasing pattern. As we can ensure the assumption of stationarity with Unit-Root test.

```{r}


par(mfrow=c(1,2))
acf(DiffUSDCADLogTranGARCH, ci.type='ma', main="ACF of 1st differnce")
pacf(DiffUSDCADLogTranGARCH, main="PACF of 1st differnce")
```


## Augmented Dickey-Fuller Test for log Tranformation Difference

```{r}
adf.test(DiffUSDCADLogTranGARCH, alternative = "stationary", k = 0)
```

##Dealing with Conditional Heteroscedaticity:
##To deal with volatile nature of bitcoin series, I have transformed the series as returns of the bitcoin.



```{r}
 
DifflogUSDCADGarch= diff(log(USJapGARCHTS))*100
plot(DifflogUSDCADGarch)
title("Plot of returns of USJapan", sub = "(2013-2018)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```

##nature as almost at all lags the p-values fall below the significance levels.


```{r}
library(TSA)
McLeod.Li.test(y= DifflogUSDCADGarch,main="McLeod-Li test statistics for Daily return series")
```



## In order to get an order of GARCH , we further transform the return series into absolute values and squared return values.


```{r}

abs = abs(DifflogUSDCADGarch)
sqr = DifflogUSDCADGarch^2
```




# GARCH Model specification:

```{r}
par(mfrow=c(1,2))
acf(abs, ci.type="ma",main=" ACF for abs. returns")
pacf(abs, main=" PACF plot for abs.returns")
```


##From ACF and PACF we see many lags are significant. Hence, we plot EACF to get the candidate models

```{r}
library(TSA)
eacf(abs) 
```

##From the squared returns ACF and PACF plot, it is not that clear to derive the order of p and q. Hence, I approach EACF and the order of ARMA are ARMA (2,3), ARMA (3,3), ARMA (2,4). Thus, GARCH candidate models would be GARCH (3,2) GARCH (3,3) GARCH (4,2)

```{r}


par(mfrow=c(1,2))
acf(sqr, ci.type="ma",main="ACF  for sqr. return")
pacf(sqr, main="PACF for sqr. return")
```

##

```{r}
eacf(sqr) 
```



### With reference to the Dickey-Fuller Test, p-value is less than the 0.02 and we can reject the null hypothesis stating the non-stationarity. Hence , we can proceed further for model selection .


#MODEL ESTIMATION:
##GARCH (2,1): for US and Japanese Curruency Pair


```{r}


# GARCH(2,1)
USDCADGARCHFit.21 = garch(DifflogUSDCADGarch,order=c(2,1),trace =FALSE)
summary(USDCADGARCHFit.21)
```



## GARCH (2,2):
##This model can be interpreted as an overfit model of GARCH(2,1) and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

```{r}


USDCADGARCHFit.22 = garch(DifflogUSDCADGarch, order =c(2,2),trace =FALSE)
summary(USDCADGARCHFit.22)
```


##GARCH (3,1):
##This model can be interpreted as an overfit model of GARCH(2,1) and GARCH (2,2). This model may not be consider to be a good fit.



```{r}

USDCADGARCHFit.31 = garch(DifflogUSDCADGarch,order=c(3,1),trace =FALSE)
summary(USDCADGARCHFit.31)
```


##GARCH (3,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

# GARCH(3,2) 

```{r}
USDCADGARCHFit.32 = garch(DifflogUSDCADGarch,order=c(3,2),trace =FALSE)
summary(USDCADGARCHFit.32)
```


## GARCH (3,3):
This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not consider to be a good fit.

# GARCH(3,3)

```{r}

USDCADGARCHFit.33 = garch(DifflogUSDCADGarch,order=c(3,3),trace =FALSE)
summary(USDCADGARCHFit.33)
```


##GARCH (1,1):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not considered to be a good fit.



```{r}

USDCADGARCHFit.11 = garch(DifflogUSDCADGarch,order=c(1,1),trace =FALSE)
summary(USDCADGARCHFit.11)
```



# Model Selection:
##Best possible model is selected by AIC scores of the models. From the below sort function, GARCH(3,1) would be the best model for the return series. From the p-value, 3.1 also has the lowest correlation


```{r}
library(dLagM)
GARCHModelSelectionUSDCAD = AIC(USDCADGARCHFit.21,USDCADGARCHFit.22 ,USDCADGARCHFit.31,USDCADGARCHFit.32,USDCADGARCHFit.33, USDCADGARCHFit.11)
sortScore(GARCHModelSelectionUSDCAD, score ="aic")
```


# Model Fitting:

```{r}
library(rugarch)
USDCADmodel3.1<-ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), 
                  mean.model = list(armaOrder = c(3,7), include.mean = TRUE), 
                  distribution.model = "norm")
                  
USDCADgarchMODEL3.1<-ugarchfit(spec=USDCADmodel3.1,data=DifflogUSJapGarch, out.sample = 100)
plot(USDCADgarchMODEL3.1,which="all")
```

##Model Diagnostics

```{r}
USDCADgarchMODEL3.1
```


## Forecasting

```{r}
forcgarchUSDCAD= ugarchforecast(USDCADgarchMODEL3.1, data = DifflogUSDCADGarch, n.ahead = 100, n.roll =10)
print(forcgarchUSDCAD)
```


## plotting

```{r}
plot(forcgarchUSDCAD, which= "all")
```

## Forecasting the rate


```{r}
RateUSDCADGarch = 81.074
  RUSDCADGARCH <-c(0.0112569 0.4556
T+2    0.0046645 0.4573
T+3   -0.0101408 0.4589
T+4   -0.0016507 0.4606
T+5    0.0026038 0.4622
T+6    0.0119094 0.4638
T+7    0.0157465 0.4653
T+8    0.0133890 0.4669
T+9    0.0060143 0.4684
T+10  -0.0005449 0.4699
T+11  -0.0021370 0.4714
T+12   0.0021341 0.4728
T+13   0.0088827 0.4743
T+14   0.0133894 0.4757
T+15   0.0127099 0.4771
T+16   0.0076703 0.4785
T+17   0.0019896 0.4798
T+18  -0.0004145 0.4812
T+19   0.0018728 0.4825
T+20   0.0069786 0.4838
T+21   0.0112341 0.4851
T+22   0.0117977 0.4864
T+23   0.0085339 0.4877
T+24   0.0039240 0.4889
T+25   0.0011991 0.4901
T+26   0.0020888 0.4913
T+27   0.0057435 0.4925
T+28   0.0094872 0.4937
T+29   0.0107635 0.4949
T+30   0.0088690 0.4960
T+31   0.0053078 0.4972
T+32   0.0026184 0.4983
T+33   0.0025742 0.4994
T+34   0.0050272 0.5005
T+35   0.0081382 0.5016
T+36   0.0097433 0.5026
T+37   0.0088506 0.5037
T+38   0.0062363 0.5047
T+39   0.0037974 0.5057
T+40   0.0031837 0.5067
T+41   0.0046903 0.5077
T+42   0.0071481 0.5087
T+43   0.0088186 0.5097
T+44   0.0086168 0.5107
T+45   0.0068062 0.5116
T+46   0.0047286 0.5126
T+47   0.0038175 0.5135
T+48   0.0046149 0.5144
T+49   0.0064626 0.5153
T+50   0.0080311 0.5162
T+51   0.0082706 0.5171
T+52   0.0071074 0.5180
T+53   0.0054285 0.5188
T+54   0.0044123 0.5197
T+55   0.0047065 0.5205
)
  USDCADPgarch= 0 
  for (i in 1:100){
    USDCADgarch =  RateUSDCADGarch *((2.71828)^(RUSDCADGARCH[i]/100))
    print(USDCADgarch)
    RateUSDCADGarch=USDCADgarch
  }
  
```














