---
title: "GARCH Model USJapan"
author: "Jane"
date: "27/04/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Forcasting Exchange Rate Using GARCH Model for US Dollar and Japenese Yen

## Reading Canadian and Japanes Currency into r
```{r}
library(readr)
library(dplyr)
USJapCurrencyGARCH <-  read.csv ("USDJPY_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateUSJapan = ("CLOSE"))

  
head(USJapCurrencyGARCH)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

USJapCurrencyGARCH$Date <- lubridate::ymd(USJapCurrencyGARCH$Date)
head(USJapCurrencyGARCH)

```



##Checking for obvious errors
```{r}
#Checking for obvious errors
which(is.na(USJapCurrencyGARCH))

```

##Converting the data set into time series object

```{r}
#Converting the data set into time series object
USJapGARCHTS<- ts(as.vector(USJapCurrencyGARCH$Rate),  frequency = 314, start= c(2000,01,03))
plot.ts(USJapGARCHTS)
title("Time Series plot of USJapTimeseries ", sub = "(2000-2020)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```


## Automatic Colleration and Partial Automatic Correlation
##The ACF plot clearly states the high correlation among successive points. It also shows a strong evidence of an existence of a trend as expected from the time series plot. The PACF plot shows one significant correlation on the plot. Unit root test proves the nature of non-stationarity of the series.


```{r}

par(mfrow=c(1,2))
acf(USJapGARCHTS, main=" ACF ")
pacf(USJapGARCHTS, main=" PACF ")
```




## Differening the series to ensure stationality

```{r}
ar(diff(USJapGARCHTS))
```



##Augmented Dickey-Fuller test
##The Augmented Dickey-Fuller test allows for higher-order autoregressive processes 

```{r}
library(tseries)
adf.test(USJapGARCHTS, alternative = "stationary", k = 0)
```

##Ensuring the stationarity of the series:
##Transformation:Natural Logarithmic transformation is one of the best approach to look for stationarity of the sereis.


```{r}


USJapLogTranGARCH<-log(USJapGARCHTS)

ar(USJapLogTranGARCH)
```


## Augmented Dickey-Fuller Test for log Tranformation

```{r}
adf.test(USJapLogTranGARCH, alternative = "stationary", k = 0)
```


## ACF and PACF for log transformation
## The ACF and PACF plot are similar to the original series and we can still suspect the non-stationarity of the series and this is also supported by Unit root test.
```{r}


par(mfrow=c(1,2))
acf(USJapLogTranGARCH, ci.type='ma', main=" ACF of transformed data")

pacf(USJapLogTranGARCH,  main="PACF of transformed data")

```


##Differencing as my next approach to achieve the stationarity of the series.


```{r}
DiffUSJapLogTranGARCH<-diff(USJapLogTranGARCH) 
ar(DiffUSJapLogTranGARCH)
```


## Runing ACF and PACF for the log transform Difference

##At the first difference of the transformed series, we can observe the plots of ACF and PACF shows a bit difference to the previous steep decreasing pattern. As we can ensure the assumption of stationarity with Unit-Root test.

```{r}


par(mfrow=c(1,2))
acf(DiffUSJapLogTranGARCH, ci.type='ma', main="ACF of 1st differnce")
pacf(DiffUSJapLogTranGARCH, main="PACF of 1st differnce")
```


## Augmented Dickey-Fuller Test for log Tranformation Difference

```{r}
adf.test(DiffUSJapLogTranGARCH, alternative = "stationary", k = 0)
```

##Dealing with Conditional Heteroscedaticity:
##To deal with volatile nature of bitcoin series, I have transformed the series as returns of the bitcoin.



```{r}
 
DifflogUSJapGarch= diff(log(USJapGARCHTS))*100
plot(DifflogUSJapGarch)
title("Plot of returns of USJapan", sub = "(2013-2018)",
      cex.main = 1.5,   font.main= 4, col.main= "blue",
      cex.sub = 0.75, font.sub = 3, col.sub = "red")
```

##nature as almost at all lags the p-values fall below the significance levels.


```{r}
library(TSA)
McLeod.Li.test(y= DifflogUSJapGarch,main="McLeod-Li test statistics for Daily return series")
```



## In order to get an order of GARCH , we further transform the return series into absolute values and squared return values.


```{r}

abs = abs(DifflogUSJapGarch)
sqr = DifflogUSJapGarch^2
```




# GARCH Model specification:

```{r}
par(mfrow=c(1,2))
acf(abs, ci.type="ma",main=" ACF for abs. returns")
pacf(abs, main=" PACF plot for abs.returns")
```


##From ACF and PACF we see many lags are significant. Hence, we plot EACF to get the candidate models

```{r}
eacf(abs) 
```

##From the squared returns ACF and PACF plot, it is not that clear to derive the order of p and q. Hence, I approach EACF and the order of ARMA are ARMA (2,3), ARMA (3,3), ARMA (2,4). Thus, GARCH candidate models would be GARCH (3,2) GARCH (3,3) GARCH (4,2)

```{r}


par(mfrow=c(1,2))
acf(sqr, ci.type="ma",main="ACF  for sqr. return")
pacf(sqr, main="PACF for sqr. return")
```

##

```{r}
eacf(sqr) 
```



### With reference to the Dickey-Fuller Test, p-value is less than the 0.02 and we can reject the null hypothesis stating the non-stationarity. Hence , we can proceed further for model selection .


#MODEL ESTIMATION:
##GARCH (2,1): for US and Japanese Curruency Pair


```{r}


# GARCH(2,1)
USJapGARCHFit.21 = garch(DifflogUSJapGarch,order=c(2,1),trace =FALSE)
summary(USJapGARCHFit.21)
```



## GARCH (2,2):
##This model can be interpreted as an overfit model of GARCH(2,1) and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

```{r}


USJapGARCHFit.22 = garch(DifflogUSJapGarch, order =c(2,2),trace =FALSE)
summary(USJapGARCHFit.22)
```


##GARCH (3,1):
##This model can be interpreted as an overfit model of GARCH(2,1) and GARCH (2,2). This model may not be consider to be a good fit.



```{r}

USJapGARCHFit.31 = garch(DifflogUSJapGarch,order=c(3,1),trace =FALSE)
summary(USJapGARCHFit.31)
```


##GARCH (3,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus this model is not consider to be a good fit.

# GARCH(3,2) 

```{r}
USJapGARCHFit.32 = garch(DifflogUSJapGarch,order=c(3,2),trace =FALSE)
summary(USJapGARCHFit.32)
```


## GARCH (3,3):
This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not consider to be a good fit.

# GARCH(3,3)

```{r}

USJapGARCHFit.33 = garch(DifflogUSJapGarch,order=c(3,3),trace =FALSE)
summary(USJapGARCHFit.33)
```


##GARCH (4,2):
##This model can be interpreted as an overfitting model and p values from residual tests confirms that residuals are highly correlated. Thus, this model is not considered to be a good fit.



```{r}

USJapGARCHFit.42 = garch(DifflogUSJapGarch,order=c(4,2),trace =FALSE)
summary(USJapGARCHFit.42)
```



# Model Selection:
##Best possible model is selected by AIC scores of the models. From the below sort function, GARCH(3,1) would be the best model for the return series. From the p-value, 3.1 also has the lowest correlation


```{r}
library(dLagM)
GARCHModelSelectionUSJap = AIC(USJapGARCHFit.21,USJapGARCHFit.22 ,USJapGARCHFit.31,USJapGARCHFit.32,USJapGARCHFit.33, USJapGARCHFit.42)
sortScore(GARCHModelSelectionUSJap, score ="aic")
```


# Model Fitting:

```{r}
library(rugarch)
USJapmodel3.1<-ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(3, 1)), 
                  mean.model = list(armaOrder = c(1, 1), include.mean = TRUE), 
                  distribution.model = "norm")
                  
USJapgarchMODEL3.1<-ugarchfit(spec=USJapmodel3.1,data=DifflogUSJapGarch, out.sample = 100)
plot(USJapgarchMODEL3.1,which="all")
```

##Model Diagnostics

```{r}
USJapgarchMODEL3.1
```


## Forecasting

```{r}
forcgarchUSJap = ugarchforecast(USJapgarchMODEL3.1, data = DiffUSJapLogTran, n.ahead = 100, n.roll =10)
print(forcgarchUSJap)
```


## plotting

```{r}
plot(forcgarchUSJap, which= "all")
```

## Forecasting the rate


```{r}
RateUSJapGarch = 81.074
  RUSJGARCH <-c(0.003425, 0.003831, 0.004176, 0.004470,0.004720, 0.004934, 0.005115, 0.005270, 0.005402, 0.005514, 0.005610, 0.005691, 0.005761, 0.005820, 0.005870, 0.005913, 0.005949, 0.005980, 0.006007, 0.006029, 0.006048, 0.006065, 0.006079, 0.006091, 0.006101, 0.006109, 0.006117, 0.006123, 0.006128, 0.006133, 0.006137, 0.006140, 0.006143, 0.006145, 0.006147, 0.006149, 0.006150, 0.006152, 0.006153, 0.006154, 0.006154, 0.006155, 0.006156, 0.006156, 0.006156, 0.006157, 0.006157, 0.006157, 0.006158, 0.006158, 0.006158, 0.006158, 0.006158, 0.006158, 0.006158, 0.006158, 0.006158, 0.006158, 0.006158, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159,
0.006159, 0.006159,0.006159,  0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159,
0.006159, 0.006159, 0.006159, 0.006159, 0.006159,  0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159, 0.006159 

)
  USJAPgarch= 0 
  for (i in 1:100){
    USJAPgarch =  RateUSJapGarch *((2.71828)^(RUSJGARCH[i]/100))
    print(USJAPgarch)
    RateUSJapGarch=USJAPgarch
  }
  
```














