---
title: "Prophet EUR And GBP"
author: "Jane"
date: "11/05/2021"
output: html_document
---




# Forcasting Exchange Rate Using Prophet Model for EUR And GBP
## Reading EUR and GBP Currency into r


```{r}
library(readr)
library(dplyr)
EURGBPProphet<-  read.csv ("EURGBP_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateEURGBP = ("CLOSE"))

  
head(EURGBPProphet)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

EURGBPProphet$Date <- lubridate::ymd(EURGBPProphet$Date)
head(EURGBPProphet)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(EURGBPProphet))

```


## Creating a new variable for Date and RateEURGBP called ds and y

```{r}
EURGBPProphet1 <- mutate (EURGBPProphet, ds = Date, y = RateEURGBP)
head (EURGBPProphet1)

```

## Plotting the EURGBPProphet Dataset


```{r}
library(ggplot2)
ggplot(EURGBPProphet, aes(x = Date, y= RateEURGBP))+
  geom_line()
```

##Since prophet expect columns to match ds and y, Selecting y and ds as a new dataframe

```{r}
EURGBPProphet1 <- select(EURGBPProphet1, "ds", "y")
head(EURGBPProphet1)
```



## Fitting model

```{r}
library(prophet)
FitEURGBPProphet <- prophet(EURGBPProphet1)
FitEURGBPProphet
```

##Making Prediction with ds column containing the date

```{r}
FutureRate_EURGBPProphet <- make_future_dataframe(FitEURGBPProphet, periods = 100)
tail(FutureRate_EURGBPProphet)
```


## Using the function predict to get the predicted values 


```{r}
EURGBPProphet_Forecast <- predict(FitEURGBPProphet, FutureRate_EURGBPProphet)
tail(EURGBPProphet_Forecast[c('ds', 'yhat', 'yhat_lower', 'yhat_upper')], 100)

```



## Ploting forecasted result

```{r}
plot(FitEURGBPProphet, EURGBPProphet_Forecast)

```

## You can use the prophet_plot_components function to see the forecast broken down into trend, weekly seasonality, and yearly seasonality.


```{r}

prophet_plot_components(FitEURGBPProphet, EURGBPProphet_Forecast)

```







