---
title: "Prophet Model EUR And JPY"
author: "Jane"
date: "11/05/2021"
output: html_document
---





# Forcasting Exchange Rate Using Prophet Model for EUR And JPY
## Reading EUR and JPY Currency into r


```{r}
library(readr)
library(dplyr)
EURJPYProphet<-  read.csv ("EURJPY_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateEURJPY= ("CLOSE"))

  
head(EURJPYProphet)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

EURJPYProphet$Date <- lubridate::ymd(EURJPYProphet$Date)
head(EURJPYProphet)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(EURJPYProphet))

```


## Creating a new variable for Date and RateEURGBP called ds and y

```{r}
EURJPYProphet1 <- mutate (EURJPYProphet, ds = Date, y = RateEURJPY)
head (EURJPYProphet1)

```

## Plotting the EURJPYProphet Dataset


```{r}
library(ggplot2)
ggplot(EURJPYProphet, aes(x = Date, y= RateEURJPY))+
  geom_line()
```

##Since prophet expect columns to match ds and y, Selecting y and ds as a new dataframe

```{r}
EURJPYProphet1 <- select(EURJPYProphet1, "ds", "y")
head(EURJPYProphet1)
```



## Fitting model

```{r}
library(prophet)
FitEURJPYProphet <- prophet(EURJPYProphet1)
FitEURJPYProphet
```

##Making Prediction with ds column containing the date

```{r}
FutureRate_EURJPYProphet <- make_future_dataframe(FitEURJPYProphet, periods = 100)
tail(FutureRate_EURJPYProphet)
```


## Using the function predict to get the predicted values 


```{r}
EURJPYProphet_Forecast <- predict(FitEURJPYProphet, FutureRate_EURJPYProphet)
tail(EURJPYProphet_Forecast[c('ds', 'yhat', 'yhat_lower', 'yhat_upper')], 100)

```



## Ploting forecasted result

```{r}
plot(FitEURJPYProphet, EURJPYProphet_Forecast)

```

## You can use the prophet_plot_components function to see the forecast broken down into trend, weekly seasonality, and yearly seasonality.


```{r}

prophet_plot_components(FitEURJPYProphet, EURJPYProphet_Forecast)

```










