---
title: "Prophet Model EUR and CAD"
author: "Jane"
date: "10/05/2021"
output: html_document
---

# Forcasting Exchange Rate Using Prophet Model for EUR And CAD
## Reading EUR and CAD Currency into r



```{r}
library(readr)
library(dplyr)
EURCADProphet<-  read.csv ("EURCAD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateEURCAD = ("CLOSE"))

  
head(EURCADProphet)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

EURCADProphet$Date <- lubridate::ymd(EURCADProphet$Date)
tail(EURCADProphet)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(EURCADProphet))

```
## Creating a new variable for Date and RateEURCAD called ds and y

```{r}
EURCADProphet1 <- mutate (EURCADProphet, ds = Date, y = RateEURCAD)
head (EURCADProphet1)

```

## Plotting the EURCADProphet Dataset


```{r}
library(ggplot2)
ggplot(EURCADProphet, aes(x = Date, y= RateEURCAD))+
  geom_line()
```

##Since prophet expect columns to match ds and y, Selecting y and ds as a new dataframe

```{r}
EURCADProphet1 <- select(EURCADProphet1, "ds", "y")
head(EURCADProphet1)
```



## Fiting model

```{r}
library(prophet)
FitEURCADProphet <- prophet(EURCADProphet1)
FitEURCADProphet
```

##Making Prediction with ds column containing the date

```{r}
FutureRate_EURCADProphet <- make_future_dataframe(FitEURCADProphet, periods = 100)
tail(FutureRate_EURCADProphet)
```


## Using the function predict to get the predicted values 


```{r}
EURCADProphet_Forecast <- predict(FitEURCADProphet, FutureRate_EURCADProphet)
tail(EURCADProphet_Forecast[c('ds', 'yhat', 'yhat_lower', 'yhat_upper')], 100)

```



## Ploting forecasted result

```{r}
plot(FitEURCADProphet, EURCADProphet_Forecast)

```

## You can use the prophet_plot_components function to see the forecast broken down into trend, weekly seasonality, and yearly seasonality.


```{r}

prophet_plot_components(FitEURCADProphet, EURCADProphet_Forecast)

```



