---
title: "Prophet Model Eur And USD"
author: "Jane"
date: "11/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Forcasting Exchange Rate Using Prophet Model for EUR And USD
## Reading EUR and USD Currency into r


```{r}
library(readr)
library(dplyr)
EURUSDProphet<-  read.csv ("EURUSD_Candlestick_1_D_BID_01.01.2000-31.12.2020.csv")%>%
  select('GMT.TIME', CLOSE)%>%
  rename(Date = ('GMT.TIME'), RateEURUSD = ("CLOSE"))

  
head(EURUSDProphet)
```

## Conversion of Gmt time to date format
```{r}
library(dplyr)
library(lubridate)

EURUSDProphet$Date <- lubridate::ymd(EURUSDProphet$Date)
head(EURUSDProphet)

```



##Checking for obvious errors or missingg value
```{r}
#Checking for obvious errors
which(is.na(EURUSDProphet))

```


## Creating a new variable for Date and RateEURUSD called ds and y

```{r}
EURUSDProphet1 <- mutate (EURUSDProphet, ds = Date, y = RateEURUSD)
head (EURUSDProphet1)

```

## Plotting the EURCADProphet Dataset


```{r}
library(ggplot2)
ggplot(EURUSDProphet, aes(x = Date, y= RateEURUSD))+
  geom_line()
```

##Since prophet expect columns to match ds and y, Selecting y and ds as a new dataframe

```{r}
EURUSDProphet1 <- select(EURUSDProphet1, "ds", "y")
head(EURUSDProphet1)
```



## Fiting model

```{r}
library(prophet)
FitEURUSDProphet <- prophet(EURUSDProphet1)
FitEURUSDProphet
```

##Making Prediction with ds column containing the date

```{r}
FutureRate_EURUSDProphet <- make_future_dataframe(FitEURUSDProphet, periods = 100)
tail(FutureRate_EURUSDProphet)
```


## Using the function predict to get the predicted values 


```{r}
EURUSDProphet_Forecast <- predict(FitEURUSDProphet, FutureRate_EURUSDProphet)
tail(EURUSDProphet_Forecast[c('ds', 'yhat', 'yhat_lower', 'yhat_upper')], 100)

```



## Ploting forecasted result

```{r}
plot(FitEURUSDProphet, EURUSDProphet_Forecast)

```

## You can use the prophet_plot_components function to see the forecast broken down into trend, weekly seasonality, and yearly seasonality.


```{r}

prophet_plot_components(FitEURUSDProphet, EURUSDProphet_Forecast)

```






